%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\PassOptionsToPackage{pdfpagelabels=false}{hyperref} 
\documentclass[10pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue, modroman]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

	
\usepackage[sc]{mathpazo}
\linespread{1.05}
\usepackage[T1]{fontenc}
%\usepackage[dvipsnames]{xcolor}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
%\usepackage{hyperref}
% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

\setlength{\topmargin}{-0.7in}
\usepackage{calc}
\setlength{\textheight}{\textheight+0.5in}
\usepackage{layout}
%\usepackage{hyperref}
\usepackage{color}
%\hypersetup{linkbordercolor = green}
%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{Olalekan}
\familyname{Ogunmolu}
\definecolor{light-blue}{rgb}{0.30,0.35,1}
\title{ %Control Systems | Robotics | Machine Learning \newline
\textbf{\textcolor{light-blue}{ %\footnotesize Rerum Cognoscere Causas: To know the causes of things.
} 
}}                               % optional, remove/comment the line if not wanted
\address{ATC 1.801, ATEC Bldg}{UT Dallas, Richardson, TX 75080}        % optional, remove/comment the line if not wanted; the "country" arguments can be omitted or provided empty 
%\fax{fax number}                             % optional, remove/comment the line if not wanted
\email{opo140030@utdallas.edu}                               % optional, remove/comment the line if not wanted
%\homepage{http://lakehanne.github.io}                         % optional, remove/comment the line if not wanted
%\extrainfo{\footnotesize http://ecs.utdallas.edu/$\sim$olalekan.ogunmolu/} 
\extrainfo{\footnotesize http://ecs.utdallas.edu/ $\sim$ opo140030}                 % optional, remove/comment the line if not wanted
%\photo[64pt][0.4pt]{EverPat}                       % optional, uncomment the line if wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Rerum Cognoscere Causas: To know the causes of things.}                                  % optional, remove/comment the line if not wanted
%	
\begin{document}
	\long\def\/*#1*/{}								% Define block comment
%\vspace{-2ex}
	%-----       resume       ---------------------------------------------------------
	\makecvtitle
	\section{Education}
	\cventry{2014--Present}{PhD in Electrical Engineering }{University of Texas at Dallas}{Richardson, TX}{United States}
	{} % arguments 3 to 6 can be left empty
	
	\cventry{2011--2012}{Master of Science in Engineering in Control Systems}{The University of Sheffield}{}{UK}{}
	
	\cventry{2000--2005}{Bachelor Of Science in Physics \& Electronics}{Adekunle Ajasin University}{Akungba}{Nigeria}{}
%
\section{Publications}
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Adwait Kulkarn, Yonas Tadesse, Xuejun Gu, Steve Jiang, and Nick Gans. \href{http://ecs.utdallas.edu/~opo140030/media/Papers/iROS2017/iROS2017.pdf}{\textcolor{blue}{A 3-DOF Soft Robot System For Frameless and Maskless Cancer Radiotherapy}}. \textit{Under Review at IEEE/RSJ International Conference on Robot and Systems}: \emph{To be presented at IROS 2017}, Vancouver, BC, Canada. September 2017.}{}
		
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nick Gans. \href{http://ecs.utdallas.edu/~opo140030/media/Papers/CASE2016/CASE2016.pdf}{\textcolor{blue}{Vision-based control of a soft-robot for Maskless Cancer Radiotherapy}}. \emph{IEEE Conference on Automation Science and Engineering (CASE)}, Fort-Worth, Texas, August 2016. %\newline
	 DOI: 10.1109/CoASE.2016.7743378}{}
	 
	%\cvitem{}{\textbf{Olalekan Ogunmolu}. \href{https://arxiv.org/pdf/1612.01607v2.pdf}{\textcolor{blue}{Review of "Continuous Finite-Time Stabilization of Translational and Rotational Double Integrators"}}. \emph{arxiv PrePrints, arxiv ID: 1612.01607v2}, May 2015.}{}
		
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nick Gans. \href{http://ecs.utdallas.edu/~opo140030/media/Papers/CASE2015/CASE2015.pdf}{\textcolor{blue}{A Real-Time Soft-Robotic Patient Positioning System for Maskless Head-and-Neck Cancer Radiotherapy}}. \emph{IEEE Conference on Automation Science and Engineering (CASE)}, Gothenburg, Sweden, August 2015. DOI: 10.1109/CoASE.2015.7294318}{}
	
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nick Gans, Steve Jiang, Xuejun Gu. \href{http://www.aapm.org/meetings/2015AM/PRAbs.asp?mid=99&aid=29621}{\textcolor{blue}{An Image-Guided Soft Robotic Patient Positioning System for Maskless Head-And-Neck Cancer Radiotherapy: A Proof-of-Concept Study}}. \emph{American Association of Physicists in Medicine (AAPM)} Annual Meeting, July 2015.}{}
	
	\cvitem{}{\textbf{Olalekan Ogunmolu}, %\href{http://lakehanne.github.io/downloads/MS_Thesis.pdf}
	{\textcolor{black}{Autonomous Navigation of a Rotor-craft unmanned aerial vehicle using machine vision.}} . \newline {MS Thesis, August. 2011. Advisor: Tony J. Dodd, University of Sheffield, England.}}{}
		
	\cvitem{}{\textbf{Olalekan Ogunmolu}, \href{http://lakehanne.github.io/downloads/BS_Thesis.pdf}{\textcolor{blue}{Single Fractional Parentage Coefficients in the sd-Shell Nuclei}} . \newline {BS Thesis, Nov. 2004. \hspace{0.5em} Advisor: Ademola Amusa, Adekunle Ajasin University, Nigeria.}}{}
	%
	\section{Invited Talks}
	\cvitem{UTSW, Dallas, TX}{A 3-DOF Neuro-Adaptive Patient Pose Correcting System For Frameless and Maskless Cancer Radiotherapy,  \emph{Physics Research Seminar Series, Radiation Oncology Department, UT Southwestern Medical Center,} Dallas, TX, USA. March 2017.}
		
	\cvitem{IEEE Arlington, TX}{Towards automated accurate patient positioning in maskless cancer radiotherapy. \emph{IEEE Computational Intelligence Society,} UT Arlington, TX, USA. December 2015.}
	
	%\section{Poster Presentations}
	%\cvitem{Texas Systems Day}{A 3-DOF Neuro-Adaptive Pose Correction System For Frameless and Maskless Cancer Radiotherapy,  \emph{Texas Systems Day, Texas A \& M University,} College Station, TX, USA. March 2017.}
	%
	\section{Experience}
	\cventry{Spring - Summer 2016}{\textbf{Hardware Integration Intern,  Amazon Robotics, North Reading} }{}{MA}{
		\newline
		%$\bullet$
		Wrote and deployed the SLAM algorithm for the Zeus mobile robot project.
		%\newline
		%$\bullet$ 
		Integrated Amazon Echo to the Hermes robot for speech-based navigation.
	%	\newline 
		%$\bullet$ 
		Designed and integrated the software architecture for the web-based \textsf{ client and server} system for the Hermes mobile robot.  Wrote the ROS codebase for GYGES Stations line scanners. % used in robots' pick and place tasks. 	
		%\newline $\bullet$ 
		Wrote test cases, and defined test procedures for 2D/3D sensors required on the new stow and sort robot development stations at Amazon FCs.
		Modeled and designed 3-D sensor plates test material in hand sketches and SolidWorks
		}{}
			%			
	\section{Awards and honors}
		\cvlistitem{\textbf{President’s Teaching Excellence Award for Teaching Assistants}  \hspace{1.0em}	 Nominated Feb. 2017}

		\cvlistitem{\textbf{IEEE RAS Travel Award} \hspace{8.0cm} August 2016}	
				
		\cvlistitem{\textbf{Ericsson Graduate Fellowship} \hspace{7.4cm} 2015 - 2016}		
			
		\cvlistitem{\textbf{Jonsson Scholarship} \hspace{9.0cm} 2014 - 2015}	
			
		\cvlistitem{\textbf{Achievement Award, University of Florida, }
		   \textit{(Declined)} \qquad \qquad \qquad \qquad \qquad \quad Fall 2014 \newline
		   Mech \& Aerospace Engineering Dept.}	
			
		\cvlistitem{\textbf{PTDF Overseas Scholarship Award [Nigeria]} \hspace{0.9cm} $\sim$1.7\% acceptance, \hspace{0.9cm} 2011 - 2012}
			
		\cvlistitem{\textbf{Federal Government (of Nigeria) Scholarship}, \hspace{0.8cm}  $\sim$3.6\%  acceptance,\hspace{1.9cm}	2002}
			
		\cvlistitem{\textbf{Ondo State (Nigeria) Scholarship} \hspace{2.8cm} $\sim$10\% acceptance, \hspace{2.0cm} 2004}
		%		
	\section{Computing}
		\cvitem{\textcolor{light-blue}{Programming}}{ C++, Python, Lua, MATLAB/LabVIEW -- in that order. \newline
		\textbf{\textendash \, C++: } \textsf{the point cloud, opencv, boost, eigen e.t.c. libraries; c++11/14 standards}.
		%
		\newline 
		\textbf{\, \textendash \, MATLAB}, \textbf{LabVIEW}: \textsf{system identification, control, signal processing, fpga, robotics modules/toolkits}
		\newline
		\textbf{\, \textendash \,Python} \textsf{SciPy tools including: \textcolor{light-blue}{matplotlib}, \textcolor{light-blue}{numpy}, and \textcolor{light-blue}{scikit learn}}.
		%
		\newline
		\textbf{\, \textendash \, Neural Network Frameworks:} \textsf{ \textbf{Torch 7} [\textcolor{light-blue}{cutorch}, \textcolor{light-blue}{cudnn}, \textcolor{light-blue}{cunn}, the \textcolor{light-blue}{display, rnn and conv-net}], and \textbf{pytorch}. Familiar with \textbf{caffe}, and \textbf{tensorflow}. }
		%
		%\newline
		%\textbf{\, \textendash \, pytorch} %\textsf{\textcolor{light-blue}{cutorch}, \textcolor{light-blue}{cudnn}, \textcolor{light-blue}{cunn}, the \textcolor{light-blue}{display, rnn and conv-net} libraries}
		} 
	
		\cvitem{\textcolor{light-blue}{*Nix OSes}}{Ubuntu, Debian. Familiar with openSUSE.}
				
		\cvitem{\textcolor{light-blue}{ROS}}{
		ROS Hydro/Indigo/Jade/Kinetic for vision, estimation, function approximation, and control tasks.
	    }
			
		\cvitem{\textcolor{light-blue}{\small Web}}{{\small HTML}, {\small Markdown. Familiar with socket.io, node.js, and express.js, } %\textcolor{light-blue}{\small Jekyll/Ruby/Hyde}.
		}
		%\cvitem{\textcolor{light-blue}{\small Github} }{ \href{https://github.com/lakehanne}{\textcolor{light-blue}{https://github.com/lakehanne}} | \href{https://github.com/service-lab}{\textcolor{light-blue}{https://github.com/service-lab}}
%			}
	%	\cvitem{\textcolor{light-blue}{\small Gitlab} }{ \href{https://gitlab.kitware.com/lakehanne}{\textcolor{light-blue}{https://gitlab.kitware.com/lakehanne}} 				}
	%	\cvitem{\textcolor{light-blue}{\small Windows}}{\small MS DOS, Win XP, 7, 8, \& 10.}
	%
	\section{Select OpenSource Contributions}	
		 	  	 
		\cvitem{\href{https://github.com/lakehanne/savitzky-golay}{\textcolor{light-blue}{savgol}}}{C++ Implementation of Savitzky-Golay Differentiation Coefficients and Filters. (Available at \href{https://github.com/lakehanne/savitzky-golay}{\textcolor{light-blue}{https://github.com/lakehanne/savitzky-golay}})%(Available on \href{https://github.com/lakehanne/savitzky-golay}{\textcolor{light-blue}{https://github.com/lakehanne/savitzky-golay}})
		}
		\cvitem{\href{https://github.com/PointCloudLibrary/pcl}{\textcolor{light-blue}{pcl}}}{The Point Cloud Library (Available at \href{https://github.com/PointCloudLibrary/pcl}{\textcolor{light-blue}{https://github.com/PointCloudLibrary/pcl}}).
			 	  }
		% 	  	 	 
		\cvitem{\href{https://github.com/lakehanne/ensenso}{\textcolor{light-blue}{ensenso}}}{ Drivers for runing the ensenso camera with the point cloud library. (Available at \href{https://github.com/lakehanne/ensenso}{\textcolor{light-blue}{https://github.com/lakehanne/ensenso}})
			 }
			 
		 \cvitem{\href{https://github.com/element-research/rnn}{\textcolor{light-blue}{rnn}}}{Recurrent Neural Networks in Torch7. (Available at \href{https://github.com/element-research/rnn}{\textcolor{light-blue}{https://github.com/element-research/rnn}})
		 	}
		 	
	 	 \cvitem{\href{https://github.com/lakehanne/savitzky-golay}{\textcolor{light-blue}{gps
	 	 			}}}{Catkinized version of Levine et. al's guided policy search algorithm in ROS Indigo (Available at \href{https://github.com/lakehanne/gps}{\textcolor{light-blue}{https://github.com/lakehanne/gps}}).
	 	 }
	 	 %
	 	 %\cvitem{\href{https://github.com/torch/nn}{\textcolor{light-blue}{Torch-NN}}}{Neural Network Library in Torch7. (Available at  \href{https://github.com/lakehanne/nn}{\textcolor{light-blue}{https://github.com/torch/nn}). 
	 	%  	 	}}	
	   
	% 	\cvitem{\href{https://github.com/lakehanne/FARNN}{\textcolor{light-blue}{FARNNs}}}{Neural Network models for Borel measurable sets. (Available at  \href{https://github.com/lakehanne/FARNN}{\textcolor{light-blue}{https://github.com/lakehanne/FARNN})
%	 	}} 	
	 
	 	%\cvitem{\href{https://github.com/lakehanne/keyence}{\textcolor{light-blue}{Keyence}}}{Minimal source code for retrieving profile map from the keyence LJV-7000 series line scanners. (Available at  \href{https://github.com/lakehanne/keyence}{\textcolor{light-blue}{https://github.com/lakehanne/keyence}) 
	 	%}}
	 	
	 	%\cvitem{An all-convolutional network}{Source codes for my entry in the Kaggle 2016 data science competition in identifying and segmenting ultrasound images of the human neck. Codes available upon request.}
	 	%
%	\section{Selected service and leadership}
%	\cventry{2015 -- 2016}{Science instructor}{IEEE Dallas Shoulder of Giants Workshops}{Dallas, TX}{}{ %Participant at IEEE Dallas Young Professionals community outreaches in promoting STEM education and awareness in the Dallas/Fort-Worth Metroplex.
%	}		
%	\cventry{Summer 2015}{Summer Science Program}{University of Texas at Dallas}{Richardson, TX}{}{ %Trained high-school kids in basic robots control and programming with the Berkeley Snap! kit and arduino.
%	}	
%	\cventry{Fall 2012}{Workshop participant}{ILA Berlin Airshow}{Berlin, Germany}{}{%Selected by Cassidian (an EADS company) for the \emph{Aerospace Systems Engineering} workshop. % based on a competitive admission process.
%		}	
%	\cventry{Summer 2012}{Workshop participant}{Farnborough International Airshow}{NE Hampshire, England}{}{ %Selected by Airbus (an EADS company) among participants at the \emph{UAV and Fighter Aircraft} workshop. % based on a competitive admission process.
%	}
%	
	\section{Other interests and activities}
	\cvline{}{Reviewer, International Federation of Automatic Control World Congress (\textbf{\textit{IFAC}}) %\hspace{6.5em}		%\newline 	
		\textsf{ Jan 2017}
	}{}
		
	\cvline{}{Most-viewed writer in Control Engineering, \textbf{\textit{Quora}}
	\textsf{ Oct/Nov. 15; Mar/April16. Dec. 16 - Now.}}{}
	
	\cvline{}{Most-viewed writer in ROS, \textbf{\textit{Quora}} \hspace{15em}
	\textsf{ June - August 2016}}{}
	
	\cvline{}{Teacher Badge \hspace{8.0em}\textbf{\textit{Stackoverflow.com}}
		%	\newline
	\hspace{10.1em}\textsf{2015 -- Present}}{}
		
	\cvline{}{Scholar Badge \hspace{8.0em}\textbf{\textit{Stackexchange.com}}
			%	\newline
	\hspace{10.1em}\textsf{2015 -- Present}}{}
	
	\renewcommand{\listitemsymbol}{-}
	\clearpage
	%-----       letter       ---------------------------------------------------------
	% recipient data
%	\recipient{Company Recruitment team}{Company's name\\Street address\\Zip Code City}
%	\date{Date}
%	\opening{Dear Sir or Madam,}
%	\closing{Yours faithfully,}
%	\enclosure{enclosures}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%	\makelettertitle
%	\makeletterclosing

\end{document}
