\section{Experience: Leadership, Hardware, and Computing}
	%
	\cvitem{\lb{Collaborator/ Team Leader}}{Experience leading/working with teams to create and execute plans to bring-up, and validate designs to achieve system level functionalities. Experience working closely with partnership teams (e.g. research and supply chain, industrial manufacturing), and external vendors by optimizing the manufacturing process for volume scale-up. Designing sensor integration, testing and calibration methodology for volume manufacturing at lowest cost, and iterating on ideas, prototype, test, refine cycle. Managing by positive influence.}
	%
	\cvitem{\lb{Innovation}}{Experience solving complex system issues, developing system requirements, driving technical innovation and roadmap. Experience gathering requirements, defining high level architecture, executing hardware design, and product validation. Experience in companies and universities(Europe, Asia, and Africa), across disciplines and industries.}
	%
	\subsection{Hardware}
	%

	\cvitem{\lb{Prototyping}}{Experience in components selection (including design and verification of programmable soft actuators, linear actuators, bike gear drivetrains, \& braking systems), sensors (MEMs, liquid metals, \& cameras and optical systems) selection and integration, microcontrollers integration (National Instruments, Raspberry Pi's, Arduinos), components specifications, schematic design, PCB layout and bring up.}

	%\cvitem{\lb{Board Design}}{Experience in board validation and with design tools (e.g. Eagle, schematic capture, layout tools, lab bring up and debug).}

	\cvitem{\lb{Embedded Systems}}{Experience with design of  embedded systems, completing board layouts, assembling, testing, debugging, and integrating designs into opto-electro-mechanical systems. Communication protocols (e.g. SPI, $I^2C$, TCP/IP, UDP), Linux/Python scripting, and C++. Enjoy being hands-on in the lab, in the details (soldering, oscilloscopes, data acquisition) and a thriving gusto for engineering.}

	\subsection{Research}	
	\cvitem{2021 - Present}{\bf{Senior Researcher}, \href{https://www.microsoft.com/en-us/research/lab/microsoft-research-new-york/}{\bl{Microsoft Research}}, New York City, NY 10012, USA.
		\newline
		%
		\footnotesize{Reinforcement Learning Group, 300 Lafayette Street, New York City, NY 10012.}
	} 
	%
	\cvitem{2019 - 2021}{\bf{Postdoctoral Scholar}, \href{https://med.upenn.edu}{\bl{The University of Pennsylvania}}, Philadelpia, PA, USA.
		\newline
		%
		\footnotesize{Department of Radiation Oncology, Perelman School of Medicine, University of Pennsylvania.}
	} 

		\cvitem{Summer '19}{\bf{Visiting Postdoctoral Scholar}, \href{https://uchicago.edu}{\bl{The University of Chicago}}, Chicago, IL, USA.
		\newline
		%
		\footnotesize{Department of Radiation and Cellular Oncology, Pritzker School of Medicine, The University of Chicago.}
	} 

	\cvitem{Summer '18}{\bf{Research Intern}, \href{https://www.preferred-networks.jp/en/}{\bl{Preferred Networks}}, Otemachi, Chiyoda-ku, Tokyo, Japan.
		\newline
		\footnotesize{\href{https://www.wsj.com/articles/attention-parents-this-robot-will-clean-up-your-childs-toys-1539602386?fbclid=IwAR2ssHpJ3GHj-_9cIXyiPNiZiranoY_Xf9q9pA0DdQb-1PuFhmDVgPzGquA}{\bl{``Preferred Networks is one of a tiny handful of Japanese `unicorns', or technology startups valued at more than \$1 billion."}} -- The Wall Street Journal, 10/15/2018}
		\newline
		%
		\footnotesize \textit{Research Intern within the Robotics Team. Worked on stable learning of complex robot motion-planning/manipulation tasks.}
		\newline
		%
		Implemented Khansari-Zadeh's CLF-DM on the Tokyo Robotics 7-DoF Arm. Proposed a DP approach for better complex robot trajectory imitation.		
	}
	
	\cvitem{Fall '17 - Spring '19}{\bf{Research Assistant}, Medical Aritificial Intelligence and Automation Laboratory, Division of Medical Physics and Engineering, Radiation Oncology Department, UT Southwestern Medical Center.
	\newline
	\footnotesize \textit{Research Assistant for Dr. Steve Jiang, Barbara Crittenden Professor of Cancer Research, UTSW Department of Radiation Oncology.}
	\newline
	Developed a multidisciplinary approach (spanning Deep learning, optimal control, dynamic programming, and game theory) in order to solve the classic beam orientation optimization (BOO) problem.
	}

	\cvitem{Summer - Fall '17}{\bf{Research Assistant}, Dr. Tyler Summers, Mechanical Engineering, UT Dallas.
		\newline
		\footnotesize {\textit{Dynamic Programming, Decision Theoretic Control, Machine/Reinforcement Learning.}}	
		\newline
		Developed a conservative controller for mitigating the lack of robustness in multi-stage decision policies.
		}
	%
	\cvitem{Fall '14 - Spring 19}{\bf{Research Assistant}, Dr. Nick Gans, Electrical Engineering, University of Texas at Dallas.
		\newline
		\footnotesize {\textit{Control Systems, Systems Identification, State Estimation and Computer Vision.}}
		\newline
		Conceived the prototypical testbed, procured hardware, integrated components to simulate soft robot compensating systems for patients in intensity modulated radiotherapy.
	}
	%
	\cvitem{Summer '16}{\bf{Hardware Integration Intern}, Amazon Robotics LLC. 
		\newline
		\footnotesize {\textit{SLAM, Software and Hardware Integration Intern% for Tye Brady, Chief Technology Officer
						}.}
		\newline
		Helped integrate the hardware and software for the P3-DX robot used as a recreational robot in the Amazon Robotics office.
	}
	%
	\cvitem{Spring '16}{\bf{Hardware Integration Intern}, Advanced Robotics Lab, Amazon Robotics LLC. 
		\newline
		\footnotesize {\textit{Hardware Integration Intern%for Dr. Andy Stubbs, Senior Hardware Systems Engineer
				}.}
		\newline
		Wrote the codebase for the line scanners used in tracking objects in amazon warehouse assembly lines.
	}
	%%
	\subsection{Computing}
	\cvitem{\textcolor{light-blue}{P.D.E.s}}{Level Set Methods: Finite Differences; Upwinding; Weighted Essentially Non-oscillatory Solutions. Deep Learning; Hamilton-Jacobi (Bellman/Isaacs) Equations. Numerical Schemes: Differential Dynamic Programming, Iterative Linearization Methods; Quazilinearization Methods.}
	%
	\cvitem{\textcolor{light-blue}{Optimal control}}{Numerical Schemes: Differential Dynamic Programming, Iterative Linearization Methods; Quasi-linearization Methods.}
	%
	\cvitem{\textcolor{light-blue}{Programming}}{ C++, Python, Lua, MATLAB, LabVIEW.}
	%
	\cvitem{\lb{Libraries}}{Point Cloud Library, OpenCV, Eigen, Docker, PyTorch, OpenAI Gym, MuJoCo, Numpy, SciPy, Scikit-Learn, C++11/14 standards.
	}
	%
	\cvitem{\lb{OS}}{OSX, Debian, Windows.}
	%
	\cvitem{\lb{OSRF}}{ROS 1.x/ROS 2.0.
	}
	%
	\cvitem{\textcolor{light-blue}{\small Web}}{{\small HTML}, {\small Markdown,  socket.io, node.js, and express.js.}
	}
	\subsection{Teaching:}
	\cventry{Spring '20 - }{Adjunct Instructor, \textbf{RBOT 250- Robot manipulation, planning and control}}{Brandeis University}{}{}{Designing course outlines and teaching.}
	%
	\cventry{Fall '14 - '16}{Teaching Assistant, \textbf{Introduction to Robotics}}{University of Texas at Dallas}{}{}{Guided students during laboratories in programming the Robai Cyton 300R2 Robot and graded homeworks.}
	%
	\cventry{Spring '15}{\textbf{Teaching Assistant, Linear Systems (M.S. Class)}}{University of Texas at Dallas}{}{}{Responsible for helping Masters students with linear control theory applications; graded homeworks and midterms.}
	%
%	\cventry{Spring '14}{\textbf{Instructor, Analysis and Design of Digital Systems}}{Adekunle Ajasin University}
%	{}{}{Developed course modules, sole instructor for sophomore students, graded homeworks, designed and graded exams.}
%	%
%	\cventry{Summer '14}{\textbf{Instructor, Digital Logic Design}}{Adekunle Ajasin University}{}{}{Co-developed course modules, joint-instructor for junior students, graded homeworks, designed and graded exams.}
	%
%	\subsection{Miscellaneous:}
%	\cventry{2009--2011}{\textbf{Warehouse Manager, Apapa Plant}}{Coca-Cola Hellenic Bottling Company Plc}{Lagos}{\newline Minimized glass breakages by 40\%, assured efficiency in supply chain operations by coordinating with the Ikeja/Head Office Logistics teams, supervised 3 Coca-Cola mega warehouse managers leading to a reduction in waste by 35\% after a 9-month stint at Apapa mega-plant. Introduced new standard operating procedures company-wide and country-wide to formalize waste minimization processes, and improve production supply chain processes. This led to the Apapa plant being the highest selling plant for all Coke categories for two consecutive quarters}{}
%	%
%	\cventry{2007--2008}{Banking Assistant}{First Bank of Nigeria Plc}{Lagos}{}{}
%	%
%	\cventry{2005--2007}{System Engineer}{DMT Technologies Limited}{KD}{Nigeria}{}
%	%
%	%	\clearpage
\subsection{Select OpenSource Projects}
\cvitem{\href{https://github.com/lakehanne/LyapunovLearner}{\textcolor{light-blue}{Lyapunov-Learner}}}{Python Implementation of ``Learning Control Lyapunov Functions for Dynamical Systems" (Available at \href{https://github.com/sorcerer/LyapunovLearner}{\textcolor{light-blue}{https://github.com/robotsorcerer/LyapunovLearner}}).
}	
%
\cvitem{\href{https://github.com/robotsorcerer/LevelSetPy}{\textcolor{light-blue}{LevelSetPy}}}{Implementations of common level set methods for computing the solutions to Hamilton-Jacobi Equations (Available at \href{https://github.com/robotsorcerer/LevelSetPy}{\lb{https://github.com/robotsorcerer/LevelSetPy}}).}{}.
%
\cvitem{\href{https://github.com/lakehanne/keyence}{\textcolor{light-blue}{Keyence}}}{Minimal source code for retrieving profile map from the keyence LJV-7000 series line scanners (Available at  \href{https://github.com/lakehanne/keyence}{\textcolor{light-blue}{https://github.com/lakehanne/keyence}).}}
%
%\cvitem{\href{https://github.com/Element-Research/rnn/blob/master/FastLSTM.lua}{\textcolor{light-blue}{RBN}}}{Recurrent Batch Normalization of Neural Networks in Torch7. (Available at \href{https://github.com/Element-Research/rnn/blob/master/FastLSTM.lua}{\textcolor{light-blue}{https://github.com/element-research/rnn}})
%}
%%
%\cvitem{\href{https://github.com/lakehanne/nn/blob/master/DICECriterion.lua}{\textcolor{light-blue}{DICE}}}{S\o{}rensen-Dice coefficients in Torch7. (Available at  \href{https://github.com/lakehanne/nn}{\textcolor{light-blue}{https://github.com/lakehanne/nn}).
%}}
%%		
%\cvitem{\href{https://github.com/lakehanne/FARNN}{\textcolor{light-blue}{FARNNs}}}{Training of multilayer networks, simple recurrent neural networks, long short-term memory cells (with peep-hole connections), fast LSTMS, %(which are LSTMs with gates computed in one fell-swoop
	%	and recurrent batch normalized FastLSTMs to model the relationship between Borel measurable sets. (Available at  \href{https://github.com/lakehanne/FARNN}{\textcolor{light-blue}{https://github.com/lakehanne/FARNN})
		%}}
%
%\cvitem{\href{https://github.com/lakehanne/awesome-neurocontrol}{\textcolor{light-blue}{Awesome-NeuroControl}}}{A curated list of neural applications in control theory and practice. (Available at \href{https://github.com/lakehanne/awesome-neurocontrol}{\textcolor{light-blue}{https://github.com/lakehanne/awesome-neurocontrol}})
	%}		
%%	
%\cvitem{\href{https://github.com/lakehanne/awesome-screw-theory}{\textcolor{light-blue}{Awesome-Screw Theory}}}{A curated list of screw theory and practice in continuum, soft and semi-rigid robots. (Available at \href{https://github.com/lakehanne/awesome-neurocontrol}{\textcolor{light-blue}{https://github.com/lakehanne/awesome-screw-theory}})
	%}			
