\section{Statement of Goals}
\subsection{Research Mission}
% A
\cvline{}{As the gig economy evolves, automating rote tasks has taken a higher priority in business value chains. Rigid robots have played an important role in this economic transformation. However, as humans increasingly share workspaces with rigid robots,  safety and robot lightness have become paramount given these robots' low transportable loads, and their links' large flexure torques which magnify errors (e.g. from shoulder out to the end-effector). These intrinsic properties hamper their use in sophisticated control strategies that require minimizing or eliminating load-dependent errors. Fixes such as the industrial stiffening process, intended to enhance  accuracy,  only contributes to a high load-to-weight ratio and complicates the actuation system. 
Soft robots, however, exhibit distributed deformation, bending and twisting capabilities, and possess hyper-redundancy in their configuration space. These make them capable of flexible manipulation in delicate workspaces; their minimal resistance to applied strain and limited load-to-weight ratio make them choice mechanisms in sensitive automation domains. 
My research goal is to harness the unique advantage that soft robots offer in real-world manipulation that rigid robots lack viz., their morphological computation properties. Cleverly exploiting these properties yield simplified control laws and human-friendly mechanical systems. I want to continue providing robust models and controllers for soft robots that serve as better alternatives to current rigid manipulation technologies. I am interested in designing 
\begin{inparaenum}[(1)]
\item robust models,
\item robust adaptive controllers, and
\item software simulation frameworks
\end{inparaenum}
that make it easier for engineers, chemists, and biologists alike to create, test, verify and validate soft continuum manipulators as designers originally envisioned.}{}

%\subsection{Outreach Mission}
%\cvline{}{Public understanding and consumption determine the impact of research. In addition to educating my students to understand the importance of programming languages research, I am interested in \emph{improving science communication} and \emph{facilitating commercialization of technical ideas}. From 2013-2015 I co-directed NeuWrite Boston, a working group of scientists and science writers. To narrow the gap between academia and industry, I co-founded the Cybersecurity Factory, an accelerator for security startups.}{}
%
%\subsection{Research Directions}
%\cvline{}{I am investigating how the following two programming models facilitate the creation of programs and analyses that were previously difficult or impossible.}{}
%\cvlistitem{\textbf{Policy-agnostic programming for security and privacy.} As an alternative to approaches for detecting information leaks, I propose a new programming model that factors out the specification of security and privacy concerns from the rest of the program and enforces the properties \emph{by construction}. In my prior work I designed a language semantics for policy-agnostic programming with \emph{informaton flow policies} and developed dynamic and static enforcement techniques. I am currently interested in
%\begin{inparaenum}[(1)]
%\item extending the approach for statistical privacy and
%\item techniques for retrofitting legacy code with the policy-agnostic model, for purposes of fixing bugs and interacting with new policies and code.
%\end{inparaenum}}
%\cvlistitem{\textbf{Rule-based programming for biological modeling.} Traditionally, researchers model intracellular signalling using systems of ordinary differential equations (ODEs), but there are two problems with ODE models. First, a precise model requires a different ODE for each interaction between agents, causing ODE models to scale poorly with respect to number of agent types. Second, ODE models have little structure that we can exploit for scale-mitigating analyses. As an alternative, rule-based languages allow the representation of models as programs describing rewrites over graphs, where nodes correspond to proteins and edges describe protein complexes. Not only are these programs more concise than the corresponding ODE systems, but their structure also supports various analyses that are otherwise not possible. My current work focuses on analyzing \emph{causal relationships} between rules, and combining causal information with language design and model-checking techniques to create biologically relevant model analyses.}
