\section{\textbf{Abstracts}:}
	\cvitem{}{Azar Sadeghnejad Barkousaraie, \textbf{Olalekan Ogunmolu}, Steve Jiang, and Dan Nguyen.  \href{}{\bl{A Fast Deep Learning Approach for Beam Orientation Selection Using Supervised Learning with Column Generation on IMRT Prostate Cancer Patients}}. \href{}{\emph{Medical Physics (AAPM)} 46 (6), E237-E237, San Antonio, TX}, July 2019.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Azar Sadeghnejad Barkousaraie, Nicholas Gans, Steve Jiang, and Dan Nguyen.  \href{}{\bl{An Approximate Policy Iteration Scheme for Beam Orientation Selection in Radiation Therapy}}. \href{}{\emph{Medical Physics (AAPM)} 46 (6), E386-E386 San Antonio, TX}, July 2019.}{}
	%
	\cvitem{}{Azar Sadeghnejad Barkousaraie, \textbf{Olalekan Ogunmolu},  Steve Jiang, and Dan Nguyen.  \href{}{\bl{A Reinforcement Learning Application of Guided Monte Carlo Tree Search Algorithm for Beam Orientation Selection in Radiation Therapy}}. \href{}{\emph{Medical Physics (AAPM)}  46 (6), E236-E236, San Antonio, TX}, July 2019.}{}
	%
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nicholas Gans, and Tyler Summers. \href{}{\bl{Minimax Iterative Dynamic Game: Application to Nonlinear Robot Control Tasks}}. \emph{IEEE International Conference on Robotics and Automation. \href{http://www.cs.unm.edu/amprg/Workshops/MLPC18/index.html}{\bl{Machine Learning for Planning and Control Workshop}} Extended Abstract } (\emph{ICRA 2018}), Madrid, Spain. October 2018.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nicholas Gans, and Tyler Summers. \bl{Minimax Iterative Dynamic Game: Application to Nonlinear Robot Control Tasks.}  \emph{IEEE International Conference on Robotics and Automation, Late Breaking Result Abstract} Brisbane, Australia, May 2018.}

	\cvitem{}{Yara Almubarak, Joshi Aniket, \bf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, Nicholas Gans, and Yonas Tadesse. \bl{Design and Development of Soft Robots for Head and Neck Cancer Radiotherapy.} \emph{\href{http://spie.org/conferences-and-exhibitions/smart-structures/nde?SSO=1}{SPIE: Smart Structures + Nondestructive Evaluation},} Denver, CO, U.S.A. March 2018.
	}

	\cvitem{}{Tyler Summers, \textbf{Olalekan Ogunmolu}, and Nicholas Gans. \bl{Robustness Margins and Robust Guided Policy Search for Deep Reinforcement Learning"}. \emph{IROS 2017 Abstract Only Track}, Vancouver, BC, Canada. September 2017.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nick Gans, Steve Jiang, and Xuejun Gu. \href{http://www.aapm.org/meetings/2015AM/PRAbs.asp?mid=99&aid=29621}{\textcolor{blue}{An Image-Guided Soft Robotic Patient Positioning System for Maskless Head-And-Neck Cancer Radiotherapy: A Proof-of-Concept Study}}. \emph{American Association of Physicists in Medicine (AAPM) Annual Meeting}, Annaheim, CA, USA. July 2015.}{}

\section{Poster Presentations:}
	\cvitem{AAPM '19}{\href{}{\textcolor{blue}{An Approximate Policy Improvement Scheme for Beam Orientation Selection in Radiation Therapy.} \newline
		\textbf{Olalekan Ogunmolu}, Azar Sadeghnejad Barkousaraie, Dan Nguyen, and Steve Jiang.} \newline
	John R. Cameron Young Investigators Symposium,  \emph{61st Annual Meeting \& Exhibition of the American Association of Physicists in Medicine (AAPM) Annual Meeting}, San Antonio, TX, USA. July 2019.}{}
	%
	\cvitem{AAPM '19}{\href{}{\textcolor{blue}{A Fast Deep Learning Approach for Beam Orientation Optimization}}. \newline
	Azar Sadeghnejad Barkousaraie, \textbf{Olalekan Ogunmolu}, Steve Jiang, and Dan Nguyen. 
	\newline \emph{61st Annual Meeting \& Exhibition of the American Association of Physicists in Medicine (AAPM) Annual Meeting}, San Antonio, TX, USA. July 2019.}{}
	%
	\cvitem{AAPM '19}{\href{}{\textcolor{blue}{A Reinforcement Learning Application of Guided Monte Carlo Tree Search Algorithm for Beam Orientation Selection in Radiation Therapy}}.  
	\newline 
	Azar Sadeghnejad Barkousaraie, \textbf{Olalekan Ogunmolu}, Steve Jiang, and Dan Nguyen. 
	\newline 
	\emph{ 61st Annual Meeting \& Exhibition of the American Association of Physicists in Medicine (AAPM) Annual Meeting}, San Antonio, TX, USA. July 2019.}{}

	\cvitem{NIPS '17}{\href{}{\textcolor{blue}{An Iterative Dynamic Game for Robust Deep Reinforcement Learning.}}  \newline
	\textbf{Olalekan Ogunmolu}, Nicholas Gans, and Tyler Summers. \newline
	\emph{Neural Information Processing Systems,} Long Beach, CA, December 2017.}

	\cvitem{TSD '17}{\href{}{\textcolor{blue}{A 3-DOF Neuro-Adaptive Pose Correction System For Frameless and Maskless Radiotherapy.}}  \newline
		\textbf{Olalekan Ogunmolu}, Nicholas Gans, and Tyler Summers. 
		\newline
	\emph{Texas Systems Day, Texas A \& M University,} College Station, TX, USA. March 2017.}
