	\section{Publications}
	%\cvitem{}{Premier IEEE Robotics and Automation Society, Algorithmic Foundations of Robotics, and Medical Physics publications (WAFR, IROS, NIPS, PhysMed, and ICRA) are highly selective venues for archival papers, similar to selective IEEE journals in visibility and strong scientific/engineering communications.}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}. 
		\href{}{\bl{A Constitutive Framework For The Representation of the Viscosity Solutions of Dirichlet-type Hamilton-Jacobi Equations.}} \href{}{\emph{Transactions in Automatic Control}}, 2022.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Shaoru Chen, and George Pappas. 
	\href{}{\bl{``Constraints-Preserving" Controllers in Large-Scale Systems.}} \href{}{\emph{International Journal of Robotics Research}}, 2022.}{}	
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}.  \href{}{\bl{A Cauchy-type Hamilton-Jacobi Successive Approximation Scheme For Reachable Sets Computation.}} \href{}{\emph{In Letters to The IEEE Control Systems Society, Presentation Option at Conference on Decision and Control, Cancun}}, Mexico. 2022.}{}	
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}.  \href{}{\bl{ComplexBRAT: Complex Backward Reach-Avoid Tubes: An Emergent Collective Behavior.}} \href{}{\emph{Workshop on the Algorithm Foundations of Robotics (WAFR) XV}}, May 2022.}{}	
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}. Xinmin Liu, Nicholas Gans,  and Rodney Wiersma,  \href{}{\bl{Mechanism and Constitutive Model of a Continuum Robot for Head and Neck Cancer Radiotherapy.}} \href{}{ \emph{IEEE International Conference on Robotics and Automation (ICRA 2020)}}, Paris, France. October 2020.}{}
	%
	\cvitem{}{Azar Sadeghnejad Barkousaraie, \textbf{Olalekan Ogunmolu}, Steve Jiang, and Dan Nguyen.  \href{}{\bl{A Fast Deep Learning Approach for Beam Orientation Selection Using Supervised Learning with Column Generation on IMRT Prostate Cancer Patients}}. \href{}{\textsl{}\emph{The International Journal of Medical Physics Research and Practice}}, 2020.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Michael Folkerts, Dan Nguyen, Nicholas Gans, and Steve Jiang.  \href{}{\bl{Deep BOO: Automating Beam Orientation Selection in Intensity Modulated Radiation Therapy}}. \textit{\bl{\href{http://algorithmic-robotics.org/wafr2018/}{Algorithmic Foundations of Robotics XIII, International Workshop}}} (\emph{WAFR}), Mérida, Mexico. December 2018.}{}
	%
	\cvitem{}{Azar Sadeghnejad Barkousaraie, \textbf{Olalekan Ogunmolu}, Steve Jiang, and Dan Nguyen.  \href{https://link.springer.com/chapter/10.1007/978-3-030-32486-5_1}{\bl{Using Supervised Learning and Guided Monte Carlo Tree Search for Beam Orientation Optimization in Radiation Therapy}}. Appeared in \textit{\bl{\href{https://link.springer.com/book/10.1007/978-3-030-32486-5}{Artificial Intelligence in Radiation Therapy (AIRT). Lecture Notes in Computer Science, vol 11850. Springer Cham}}}, 2019.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Michael Folkerts, Dan Nguyen, Nicholas Gans, and Steve Jiang.  \href{}{\bl{Deep BOO: Automating Beam Orientation Selection in Intensity Modulated Radiation Therapy}}. \textit{\bl{\href{http://algorithmic-robotics.org/wafr2018/}{Algorithmic Foundations of Robotics XIII, International Workshop}}} (\emph{WAFR}), Mérida, Mexico. December 2018.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nicholas Gans, and Tyler Summers. \href{}{\bl{Minimax Iterative Dynamic Game: Application to Nonlinear Robot Control Tasks}}. \textit{IEEE/RSJ International Conference on Intelligent Robots and Systems} (\emph{IROS}), Madrid, Spain. October 2018. DOI: 10.1109/IROS.2018.8594037.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Adwait Kulkarn, Yonas Tadesse, Xuejun Gu, Steve Jiang, and Nick Gans. \href{https://arxiv.org/abs/1703.03821}{\bl{Soft-NeuroAdapt: A 3-DOF Neuro-Adaptive Pose Correction System For Frameless and Maskless Cancer Radiotherapy}}. \textit{IEEE/RSJ International Conference on Intelligent Robots and Systems} (\emph{IROS}), Vancouver, BC, Canada. September 2017. DOI: 10.1109/IROS.2017.8206211.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nicholas Gans, and Tyler Summers. \href{}{\bl{\href{https://arxiv.org/abs/1710.00491}{Robust Zero-Sum Deep Reinforcement Learning}}}. \emph{arxiv PrePrints, arxiv ID:1710.00491}, Oct 2017.}{}
	%
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nicholas Gans. \href{}{\bl{\href{https://arxiv.org/abs/1610.01439}{Nonlinear Systems Identification Using Deep Dynamic Neural Networks}}}. \emph{arxiv PrePrints, arxiv ID:1610.01439}, Oct 2016.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nick Gans. \href{http://ecs.utdallas.edu/~opo140030/media/Papers/CASE2016/CASE2016.pdf}{\bl{Vision-based control of a soft-robot for Maskless Cancer Radiotherapy}}. \emph{IEEE Conference on Automation Science and Engineering (CASE)}, Fort-Worth, Texas, August 2016.  DOI: 10.1109/CoASE.2016.7743378.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nick Gans. \href{http://ecs.utdallas.edu/~opo140030/media/Papers/CASE2015/CASE2015.pdf}{\bl{A Real-Time Soft-Robotic Patient Positioning System for Maskless Head-and-Neck Cancer Radiotherapy}}. \emph{IEEE Conference on Automation Science and Engineering (CASE)}, Gothenburg, Sweden, August 2015. DOI: 10.1109/CoASE.2015.7294318.}{}
	%
	\cvitem{}{Azar Sadeghnejad Barkousaraie,  \textbf{Olalekan Ogunmolu}, Steve Jiang, and Dan Nguyen.  \href{}{\bl{Using supervised learning and guided Monte Carlo tree search for beam orientation optimization in radiation therapy}}. Under review at \textit{\bl{\href{http://iccr-mcma.org/iccr2019/}{International Conference on Medical Image Computing and Computer Assisted Intervention, XXII}}} (\emph{MICCAI}), Shenzhen, China. October 2019.}{}
	%
	\cvitem{}{Azar Sadeghnejad Barkousaraie,  \textbf{Olalekan Ogunmolu}, Steve Jiang, and Dan Nguyen.  \href{}{\bl{Deep Learning Neural Network for Beam Orientation Optimization}}. To appear in \textit{\bl{\href{http://iccr-mcma.org/iccr2019/}{International Conference on the use of Computers in Radiation Therapy XVI}}} (\emph{ICCR}), Montreal, CA. June 2019.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Dan Nguyen, Xun Jia, Weiguo Lu, Nick Gans, and Steve Jiang. \href{}{\bl{Automating Beam Orientation Optimization for IMRT Treatment Planning: A Deep Reinforcement Learning Approach}}. 
	\textit{60th Annual Meeting of the American Association of Physicists in Medicine}, Nashville, TN (\emph{AAPM}). July 2018.}{}
  	%
	\cvitem{}{Yara Almubarak, Joshi Aniket, \bf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, Nicholas Gans, and Yonas Tadesse, \bl{Design and Development of Soft Robots for Head and Neck Cancer Radiotherapy.} \emph{\href{http://spie.org/conferences-and-exhibitions/smart-structures/nde?SSO=1}{\bl{SPIE: Smart Structures + Nondestructive Evaluation}},} Denver, CO, U.S.A. March 2018. }
	%
	\section{\textbf{Abstracts}:}
	\cvitem{}{Azar Sadeghnejad Barkousaraie, \textbf{Olalekan Ogunmolu}, Steve Jiang, and Dan Nguyen.  \href{}{\bl{A Fast Deep Learning Approach for Beam Orientation Selection Using Supervised Learning with Column Generation on IMRT Prostate Cancer Patients}}. \href{}{\emph{Medical Physics (AAPM)} 46 (6), E237-E237, San Antonio, TX}, July 2019.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Azar Sadeghnejad Barkousaraie, Nicholas Gans, Steve Jiang, and Dan Nguyen.  \href{}{\bl{An Approximate Policy Iteration Scheme for Beam Orientation Selection in Radiation Therapy}}. \href{}{\emph{Medical Physics (AAPM)} 46 (6), E386-E386 San Antonio, TX}, July 2019.}{}
	%
	\cvitem{}{Azar Sadeghnejad Barkousaraie, \textbf{Olalekan Ogunmolu},  Steve Jiang, and Dan Nguyen.  \href{}{\bl{A Reinforcement Learning Application of Guided Monte Carlo Tree Search Algorithm for Beam Orientation Selection in Radiation Therapy}}. \href{}{\emph{Medical Physics (AAPM)}  46 (6), E236-E236, San Antonio, TX}, July 2019.}{}
	%
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nicholas Gans, and Tyler Summers. \href{}{\bl{Minimax Iterative Dynamic Game: Application to Nonlinear Robot Control Tasks}}. \emph{IEEE International Conference on Robotics and Automation. \href{http://www.cs.unm.edu/amprg/Workshops/MLPC18/index.html}{\bl{Machine Learning for Planning and Control Workshop}} Extended Abstract } (\emph{ICRA 2018}), Madrid, Spain. October 2018.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nicholas Gans, and Tyler Summers. \bl{Minimax Iterative Dynamic Game: Application to Nonlinear Robot Control Tasks.}  \emph{IEEE International Conference on Robotics and Automation, Late Breaking Result Abstract} Brisbane, Australia, May 2018.}

	\cvitem{}{Yara Almubarak, Joshi Aniket, \bf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, Nicholas Gans, and Yonas Tadesse. \bl{Design and Development of Soft Robots for Head and Neck Cancer Radiotherapy.} \emph{\href{http://spie.org/conferences-and-exhibitions/smart-structures/nde?SSO=1}{SPIE: Smart Structures + Nondestructive Evaluation},} Denver, CO, U.S.A. March 2018.
	}

	\cvitem{}{Tyler Summers, \textbf{Olalekan Ogunmolu}, and Nicholas Gans. \bl{Robustness Margins and Robust Guided Policy Search for Deep Reinforcement Learning"}. \emph{IROS 2017 Abstract Only Track}, Vancouver, BC, Canada. September 2017.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nick Gans, Steve Jiang, and Xuejun Gu. \href{http://www.aapm.org/meetings/2015AM/PRAbs.asp?mid=99&aid=29621}{\textcolor{blue}{An Image-Guided Soft Robotic Patient Positioning System for Maskless Head-And-Neck Cancer Radiotherapy: A Proof-of-Concept Study}}. \emph{American Association of Physicists in Medicine (AAPM) Annual Meeting}, Annaheim, CA, USA. July 2015.}{}
		
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}. \href{}{\bl{Towards Real-Time Motion Compensation in Radio-Transparent Robotic Radiation Therapy.}} \href{}{Technical Report}, November 2019.}{}
