	\section{Invited Talks}
	%\subsection{Presentations:}
	%\cvitem{UC Berkeley}{\bl{\href{}{Deep BOO! Automating Beam Orientation Optimization in Intensity-Modulated Radiation Therapy}}.
	%\newline 	{University of Carlifornia, Berkeley, CA, USA. March 2019.}}

	\cvitem{Open Robotics}{\bl{\href{}{Soft-Robotic Position Correction Mechanisms in Intensity-Modulated Radiation Therapy}}.
	\newline 	{Open Robotics Foundation, Mountain View, CA, USA. January 2019.}}

	\cvitem{Stanford University}{\bl{\href{}{Robotic Radiotherapy: Automating Position Correction in Intensity-Modulated Radiation Therapy}}.
	\newline 	{Department of Energy Resources Engineering, Stanford University, Stanford, CA, USA. November 2018.}}

	\cvitem{UChicago}{\bl{\href{}{Robotic Radiotherapy: Automating Position Correction in Intensity-Modulated Radiation Therapy}}.
	\newline 	{Department of Radiation and Cellular Oncology, The University of Chicago, Chicago, IL, USA. November 2018.}}

	\cvitem{ATR CNS Labs}{\bl{\href{}{Minimax Iterative Dynamic Game}}.
	\newline 	{Department of Brain Robot Interface, Computational Neuroscience Labs, ATR, Osaka, Japan. August 2018.}}
	
	\cvitem{Preferred Networks}{\bl{\href{}{Neural Networks and Adaptive Control}}.
	\newline 	{Preferred Networks Tech. Talk, Chiyoda-ku, Tokyo. Japan. August 2018.}}

	\cvitem{Google}{\bl{\href{http://www.utdallas.edu/~opo140030/media/Papers/Presentations/Google/google.pdf}{SoftNeuroAdapt: A 3-DoF Neuro-Adaptive Healthcare System}}.
	\newline 	\emph{Work presented by Nick Gans}, Google Robotics, Mountain View, CA. USA. September 2017.}
	%
	\cvitem{UTARI}{\bl{\href{}{A Wearable Soft Robotic Modular System for Head and Neck Motion Correction in Intensity-Modulated Radiation Therapy}}.
		\newline 	{University of Texas at Arlington Research Institute, Fort Worth, Texas, USA. May 2019.}}
	%
	\cvitem{EFSC'17, Vancouver}{Soft Robotic Modules as Position Correcting Mechanisms in Cancer RT.
    \newline
	\emph{\bl{\href{http://www.iros2017.org/program/forums/efsc}{3rd Entrepreneurship Forum \& Start-up Competition, EFSC'17,}}} Vancouver, BC, Canada. September 2017.}

	\cvitem{UTSW, Dallas, TX}{\bl{\href{http://scr.tamu.edu/?page_id=687}{A 3-DOF Neuro-Adaptive Patient Pose Correcting System For Frameless and Maskless Cancer Radiotherapy}}, \newline  \emph{Physics Research Seminar Series, Radiation Oncology Department, UT Southwestern Medical Center,} Dallas, TX, USA. March 2017.}

	\cvitem{IEEE Arlington, TX}{\bl{Towards automated accurate patient positioning in maskless cancer radiotherapy}. \newline
	\emph{IEEE Computational Intelligence Society,} UT Arlington, TX, USA. December 2015.}
