%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\PassOptionsToPackage{pdfpagelabels=false}{hyperref} 
\documentclass[10pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[orange, modroman]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

\usepackage[sc]{mathpazo}
\linespread{1.05}
\usepackage[T1]{fontenc}
%\usepackage[dvipsnames]{xcolor}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
%\usepackage{hyperref}
% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

\setlength{\topmargin}{-0.7in}
\usepackage{calc}
\setlength{\textheight}{\textheight+0.5in}
\usepackage{layout}
%\usepackage{hyperref}
\usepackage{color}
%\hypersetup{linkbordercolor = green}
%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{Olalekan}
\familyname{Ogunmolu}
\definecolor{light-blue}{rgb}{0.30,0.35,1}
%\address{ATC 1.801, ATEC Bldg}{UT Dallas, Richardson, TX 75080}       
\email{opo140030@utdallas.edu}                               % optional,
\extrainfo{\footnotesize http://ecs.utdallas.edu/ $\sim$ opo140030}      
\include{def}


\begin{document}
%\vspace{-2ex}
	%-----       resume       ---------------------------------------------------------
	%\makecvtitle
	\section{Education}
	\cventry{2014--Present}{PhD in Electrical Engineering }{University of Texas at Dallas}{Richardson, TX}{United States}
	{} % arguments 3 to 6 can be left empty
	%
	\cventry{2011--2012}{Master of Science in Engineering in Control Systems}{The University of Sheffield}{}{UK}{}
	%
	\cventry{2000--2005}{Bachelor Of Science in Physics \& Electronics}{Adekunle Ajasin University}{Akungba}{Nigeria}{}
%
\section{Publications}
\cvitem{}{Azar Sadeghnejad Barkousaraie, \textbf{Olalekan Ogunmolu}, Steve Jiang, and Dan Nguyen.  \href{}{\bl{A Fast Deep Learning Approach for Beam Orientation Selection Using Supervised Learning with Column Generation on IMRT Prostate Cancer Patients}}. \href{}{Under review at \emph{Medical Physics}}, April 2019.}{}
%
\cvitem{}{Azar Sadeghnejad Barkousaraie,  \textbf{Olalekan Ogunmolu}, Steve Jiang, and Dan Nguyen.  \href{}{\bl{Deep BOO: Using supervised learning and guided Monte Carlo tree search for beam orientation optimization in radiation therapy}}. Under review at \textit{\bl{\href{http://iccr-mcma.org/iccr2019/}{International Conference on Medical Image Computing and Computer Assisted Intervention, XXII}}} (\emph{MICCAI}), Shenzhen, China. October 2019.}{}
	
\cvitem{}{Azar Sadeghnejad Barkousaraie,  \textbf{Olalekan Ogunmolu}, Steve Jiang, and Dan Nguyen.  \href{}{\bl{Deep Learning Neural Network for Beam Orientation Optimization}}. To appear in \textit{\bl{\href{http://iccr-mcma.org/iccr2019/}{International Conference on the use of Computers in Radiation Therapy XVI}}} (\emph{ICCR}), Montreal, CA. June 2019.}{}
%
\cvitem{}{\textbf{Olalekan Ogunmolu}, Azar Sadeghnejad Barkousaraie, Dan Nguyen, Nicholas Gans, and Steve Jiang.  \href{}{\bl{A Monte Carlo Tree Game for Beam Orientation Optimization}}. To appear in \textit{\bl{\href{https://iccr-mcma.org/mcma2019/}{International Conference on the use of Computers in Radiation Therapy XVI}}} (\emph{ICCR}), Montreal, CA. June 2019.}{}
%	
\cvitem{}{\textbf{Olalekan Ogunmolu}, Michael Folkerts, Dan Nguyen, Nicholas Gans, and Steve Jiang.  \href{}{\bl{Deep BOO: Automating Beam Orientation Selection in Intensity Modulated Radiation Therapy}}. To appear at \textit{\bl{\href{http://algorithmic-robotics.org/wafr2018/}{Algorithmic Foundations of Robotics XIII, International Workshop}}} (\emph{WAFR}), Mérida, Mexico. December 2018.}{}
%
\cvitem{}{\textbf{Olalekan Ogunmolu}, Nicholas Gans, and Tyler Summers. \href{}{\bl{Minimax Iterative Dynamic Game: Application to Nonlinear Robot Control Tasks}}. \textit{IEEE/RSJ International Conference on Intelligent Robots and Systems} (\emph{IROS}), Madrid, Spain. October 2018. DOI: 10.1109/IROS.2018.8594037}{}
%
\cvitem{}{\textbf{Olalekan Ogunmolu}, Dan Nguyen, Xun Jia, Weiguo Lu, Nick Gans, and Steve Jiang. \href{}{\bl{Automating Beam Orientation Optimization for IMRT Treatment Planning: A Deep Reinforcement Learning Approach}}. 
\newline
Selected for Oral Presentation at the \textit{John R. Cameron Young Investigators Symposium -- 60th Annual Meeting of the American Association of Physicists in Medicine}, Nashville, TN (\emph{AAPM}). July 2018.}{}

\cvitem{}{Yara Almubarak, Joshi Aniket, \bf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, Nicholas Gans, and Yonas Tadesse, \bl{Design and Development of Soft Robots for Head and Neck Cancer Radiotherapy.} \emph{\href{http://spie.org/conferences-and-exhibitions/smart-structures/nde?SSO=1}{\bl{SPIE: Smart Structures + Nondestructive Evaluation}},} Denver, CO, U.S.A. March 2018.
		}
%
\cvitem{}{\textbf{Olalekan Ogunmolu}, Adwait Kulkarn, Yonas Tadesse, Xuejun Gu, Steve Jiang, and Nick Gans. \href{https://arxiv.org/abs/1703.03821}{\bl{Soft-NeuroAdapt: A 3-DOF Neuro-Adaptive Pose Correction System For Frameless and Maskless Cancer Radiotherapy}}. \textit{IEEE/RSJ International Conference on Intelligent Robots and Systems} (\emph{IROS}), Vancouver, BC, Canada. September 2017. DOI: 10.1109/IROS.2017.8206211.}{}
%
\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nick Gans. \href{http://ecs.utdallas.edu/~opo140030/media/Papers/CASE2016/CASE2016.pdf}{\bl{Vision-based control of a soft-robot for Maskless Cancer Radiotherapy}}. \emph{IEEE Conference on Automation Science and Engineering (CASE)}, Fort-Worth, Texas, August 2016. %\newline
		DOI: 10.1109/CoASE.2016.7743378.}{}
%
%\cvitem{}{\textbf{Olalekan Ogunmolu},
%	{\bl{Autonomous Navigation of a Rotor-craft unmanned aerial vehicle using machine vision.}} . \newline {MS Thesis, August. 2011. Advisor: Tony J. Dodd, University of Sheffield, England.}}{}
%%
%\cvitem{}{\textbf{Olalekan Ogunmolu}, \href{http://lakehanne.github.io/downloads/BS_Thesis.pdf}{\bl{Single Fractional Parentage Coefficients in the sd-Shell Nuclei}} . \newline {BS Thesis, Nov. 2004. \hspace{0.5em} Advisor: Ademola Amusa, Adekunle Ajasin University, Nigeria.}}{}

	%
	\section{Invited Talks}
		\cvitem{Open Robotics}{\bl{\href{}{Soft-Robotic Position Correction Mechanisms in Intensity-Modulated Radiation Therapy}}.
		\newline 	{Open Robotics Foundation, Mountain View, CA, USA. January 2019.}}
	
	\cvitem{Stanford University}{\bl{\href{}{Robotic Radiotherapy: Automating Position Correction in Intensity-Modulated Radiation Therapy}}.
 	{Department of Energy Resources Engineering, Stanford University, Stanford, CA, USA. November 2018.}}
 	
	\cvitem{UChicago}{\bl{\href{}{Robotic Radiotherapy: Automating Position Correction in Intensity-Modulated Radiation Therapy}}. 	{Department of Radiation and Cellular Oncology, The University of Chicago, Chicago, IL, USA. November 2018.}}

	\cvitem{ATR CNS Labs}{\bl{\href{}{Minimax Iterative Dynamic Game}}.
	 	{Department of Brain Robot Interface, Computational Neuroscience Labs, ATR, Osaka, Japan. August 2018.}}
	
	\cvitem{UTSW, Dallas, TX}{A 3-DOF Neuro-Adaptive Patient Pose Correcting System For Frameless and Maskless Cancer Radiotherapy,  \emph{Physics Research Seminar Series, Radiation Oncology Department, UT Southwestern Medical Center,} Dallas, TX, USA. March 2017.}
		
	\cvitem{IEEE Arlington, TX}{Towards automated accurate patient positioning in maskless cancer radiotherapy. \emph{IEEE Computational Intelligence Society,} UT Arlington, TX, USA. December 2015.}
	\section{Experience}
	\cventry{Spring - Summer 2016}{\textbf{Hardware Integration Intern,  Amazon Robotics, North Reading} }{}{MA}{
		\newline
		%$\bullet$
		Wrote and deployed the SLAM algorithm for the Zeus mobile robot project.
		%\newline
		%$\bullet$ 
		Integrated Amazon Echo to the Hermes robot for speech-based navigation.
	%	\newline 
		%$\bullet$ 
		Designed and integrated the software architecture for the web-based \textsf{ client and server} system for the Hermes mobile robot.  Wrote the ROS codebase for GYGES Stations line scanners. % used in robots' pick and place tasks. 	
		%\newline $\bullet$ 
		Wrote test cases, and defined test procedures for 2D/3D sensors required on the new stow and sort robot development stations at Amazon FCs.
		Modeled and designed 3-D sensor plates test material in hand sketches and SolidWorks
		}{}
			%			
	\section{Awards and honors}
		\cvlistitem{\textbf{President’s Teaching Excellence Award for Teaching Assistants}  \hspace{1.0em}	 Nominated Feb. 2017}

		\cvlistitem{\textbf{IEEE RAS Travel Award} \hspace{8.0cm} August 2016}	
				
		\cvlistitem{\textbf{Ericsson Graduate Fellowship} \hspace{7.4cm} 2015 - 2016}		
			
		\cvlistitem{\textbf{Jonsson Scholarship} \hspace{9.0cm} 2014 - 2015}	
			
		\cvlistitem{\textbf{Achievement Award, University of Florida, }
		   \textit{(Declined)} \qquad \qquad \qquad \qquad \qquad \quad Fall 2014 \newline
		   Mech \& Aerospace Engineering Dept.}	
			
		\cvlistitem{\textbf{PTDF Overseas Scholarship Award [Nigeria]} \hspace{0.9cm} $\sim$1.7\% acceptance, \hspace{0.9cm} 2011 - 2012}
			
		\cvlistitem{\textbf{Federal Government (of Nigeria) Scholarship}, \hspace{0.8cm}  $\sim$3.6\%  acceptance,\hspace{1.9cm}	2002}
			
		\cvlistitem{\textbf{Ondo State (Nigeria) Scholarship} \hspace{2.8cm} $\sim$10\% acceptance, \hspace{2.0cm} 2004}
		%		
	\section{Computing}
		\cvitem{\textcolor{light-blue}{Programming}}{ C++, Python, Lua, MATLAB/LabVIEW -- in that order. \newline
		\textbf{\textendash \, C++: } \textsf{the point cloud, opencv, boost, eigen e.t.c. libraries; c++11/14 standards}.
		%
		\newline 
		\textbf{\, \textendash \, MATLAB}, \textbf{LabVIEW}: \textsf{system identification, control, signal processing, fpga, robotics modules/toolkits}
		\newline
		\textbf{\, \textendash \,Python} \textsf{SciPy tools including: \textcolor{light-blue}{matplotlib}, \textcolor{light-blue}{numpy}, and \textcolor{light-blue}{scikit learn}}.
		%
		\newline
		\textbf{\, \textendash \, Neural Network Frameworks:} \textsf{ \textbf{Torch 7} [\textcolor{light-blue}{cutorch}, \textcolor{light-blue}{cudnn}, \textcolor{light-blue}{cunn}, the \textcolor{light-blue}{display, rnn and conv-net}], and \textbf{pytorch}. Familiar with \textbf{caffe}, and \textbf{tensorflow}. }
		%
		%\newline
		%\textbf{\, \textendash \, pytorch} %\textsf{\textcolor{light-blue}{cutorch}, \textcolor{light-blue}{cudnn}, \textcolor{light-blue}{cunn}, the \textcolor{light-blue}{display, rnn and conv-net} libraries}
		} 
	
		\cvitem{\textcolor{light-blue}{*Nix OSes}}{Ubuntu, Debian. Familiar with openSUSE.}
				
		\cvitem{\textcolor{light-blue}{ROS}}{
		ROS Hydro/Indigo/Jade/Kinetic for vision, estimation, function approximation, and control tasks.
	    }
			
		\cvitem{\textcolor{light-blue}{\small Web}}{{\small HTML}, {\small Markdown. Familiar with socket.io, node.js, and express.js, } %\textcolor{light-blue}{\small Jekyll/Ruby/Hyde}.
		}
		%\cvitem{\textcolor{light-blue}{\small Github} }{ \href{https://github.com/lakehanne}{\textcolor{light-blue}{https://github.com/lakehanne}} | \href{https://github.com/service-lab}{\textcolor{light-blue}{https://github.com/service-lab}}
%			}
	%	\cvitem{\textcolor{light-blue}{\small Gitlab} }{ \href{https://gitlab.kitware.com/lakehanne}{\textcolor{light-blue}{https://gitlab.kitware.com/lakehanne}} 				}
	%	\cvitem{\textcolor{light-blue}{\small Windows}}{\small MS DOS, Win XP, 7, 8, \& 10.}
	%
	\section{Select OpenSource Contributions}	
		 	  	 
		\cvitem{\href{https://github.com/lakehanne/savitzky-golay}{\textcolor{light-blue}{savgol}}}{C++ Implementation of Savitzky-Golay Differentiation Coefficients and Filters. (Available at \href{https://github.com/lakehanne/savitzky-golay}{\textcolor{light-blue}{https://github.com/lakehanne/savitzky-golay}})%(Available on \href{https://github.com/lakehanne/savitzky-golay}{\textcolor{light-blue}{https://github.com/lakehanne/savitzky-golay}})
		}
		\cvitem{\href{https://github.com/PointCloudLibrary/pcl}{\textcolor{light-blue}{pcl}}}{The Point Cloud Library (Available at \href{https://github.com/PointCloudLibrary/pcl}{\textcolor{light-blue}{https://github.com/PointCloudLibrary/pcl}}).
			 	  }
		% 	  	 	 
		\cvitem{\href{https://github.com/lakehanne/ensenso}{\textcolor{light-blue}{ensenso}}}{ Drivers for runing the ensenso camera with the point cloud library. (Available at \href{https://github.com/lakehanne/ensenso}{\textcolor{light-blue}{https://github.com/lakehanne/ensenso}})
			 }
			 
		 \cvitem{\href{https://github.com/element-research/rnn}{\textcolor{light-blue}{rnn}}}{Recurrent Neural Networks in Torch7. (Available at \href{https://github.com/element-research/rnn}{\textcolor{light-blue}{https://github.com/element-research/rnn}})
		 	}
		 	
	 	 \cvitem{\href{https://github.com/lakehanne/savitzky-golay}{\textcolor{light-blue}{gps
	 	 			}}}{Catkinized version of Levine et. al's guided policy search algorithm in ROS Indigo (Available at \href{https://github.com/lakehanne/gps}{\textcolor{light-blue}{https://github.com/lakehanne/gps}}).
	 	 }
	 	 %
	 	 %\cvitem{\href{https://github.com/torch/nn}{\textcolor{light-blue}{Torch-NN}}}{Neural Network Library in Torch7. (Available at  \href{https://github.com/lakehanne/nn}{\textcolor{light-blue}{https://github.com/torch/nn}). 
	 	%  	 	}}	
	   
	% 	\cvitem{\href{https://github.com/lakehanne/FARNN}{\textcolor{light-blue}{FARNNs}}}{Neural Network models for Borel measurable sets. (Available at  \href{https://github.com/lakehanne/FARNN}{\textcolor{light-blue}{https://github.com/lakehanne/FARNN})
%	 	}} 	
	 
	 	%\cvitem{\href{https://github.com/lakehanne/keyence}{\textcolor{light-blue}{Keyence}}}{Minimal source code for retrieving profile map from the keyence LJV-7000 series line scanners. (Available at  \href{https://github.com/lakehanne/keyence}{\textcolor{light-blue}{https://github.com/lakehanne/keyence}) 
	 	%}}
	 	
	 	%\cvitem{An all-convolutional network}{Source codes for my entry in the Kaggle 2016 data science competition in identifying and segmenting ultrasound images of the human neck. Codes available upon request.}
	 	%
%	\section{Selected service and leadership}
%	\cventry{2015 -- 2016}{Science instructor}{IEEE Dallas Shoulder of Giants Workshops}{Dallas, TX}{}{ %Participant at IEEE Dallas Young Professionals community outreaches in promoting STEM education and awareness in the Dallas/Fort-Worth Metroplex.
%	}		
%	\cventry{Summer 2015}{Summer Science Program}{University of Texas at Dallas}{Richardson, TX}{}{ %Trained high-school kids in basic robots control and programming with the Berkeley Snap! kit and arduino.
%	}	
%	\cventry{Fall 2012}{Workshop participant}{ILA Berlin Airshow}{Berlin, Germany}{}{%Selected by Cassidian (an EADS company) for the \emph{Aerospace Systems Engineering} workshop. % based on a competitive admission process.
%		}	
%	\cventry{Summer 2012}{Workshop participant}{Farnborough International Airshow}{NE Hampshire, England}{}{ %Selected by Airbus (an EADS company) among participants at the \emph{UAV and Fighter Aircraft} workshop. % based on a competitive admission process.
%	}
%	
	\section{Other interests and activities}
	\cvline{}{Reviewer, International Federation of Automatic Control World Congress (\textbf{\textit{IFAC}}) %\hspace{6.5em}		%\newline 	
		\textsf{ Jan 2017}
	}{}
		
	\cvline{}{Most-viewed writer in Control Engineering, \textbf{\textit{Quora}}
	\textsf{ Oct/Nov. 15; Mar/April16. Dec. 16 - Now.}}{}
	
	\cvline{}{Most-viewed writer in ROS, \textbf{\textit{Quora}} \hspace{15em}
	\textsf{ June - August 2016}}{}
	
	\cvline{}{Teacher Badge \hspace{8.0em}\textbf{\textit{Stackoverflow.com}}
		%	\newline
	\hspace{10.1em}\textsf{2015 -- Present}}{}
		
	\cvline{}{Scholar Badge \hspace{8.0em}\textbf{\textit{Stackexchange.com}}
			%	\newline
	\hspace{10.1em}\textsf{2015 -- Present}}{}
	
	\renewcommand{\listitemsymbol}{-}
	\clearpage
	%-----       letter       ---------------------------------------------------------
	% recipient data
%	\recipient{Company Recruitment team}{Company's name\\Street address\\Zip Code City}
%	\date{Date}
%	\opening{Dear Sir or Madam,}
%	\closing{Yours faithfully,}
%	\enclosure{enclosures}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%	\makelettertitle
%	\makeletterclosing

\end{document}
