	\section{Experience}
	\subsection{Research:}
	\cvitem{Summer 18}{\bf{Research Intern}, Preferred Networks, Tokyo, Japan.
		\newline
		\footnotesize \textit{Research Intern within the Robotics Team. Working on stable learning of complex robot motion-planning/manipulation tasks.}
	}
	
	\cvitem{Fall 17 - Present}{\bf{Visiting Research Student}, Medical Aritificial Intelligence and Automation Laboratory, Division of Medical Physics and Engineering, Radiation Oncology Department, UT Southwestern Medical Center.
	\newline
	\footnotesize \textit{Research Assistant for Dr. Steve Jiang, Barbara Crittenden Professor of Cancer Research, UTSW Department of Radiation Oncology}
	}

	\cvitem{Summer - Fall '17}{\bf{Research Assistant}, Dr. Tyler Summers, Mechanical Engineering, UT Dallas.
		\newline
		\textsf{Dynamic Programming, Decision Theoretic Control, Machine/Reinforcement Learning.}	}
	%
	\cvitem{Fall '14 - Now}{\bf{Research Assistant}, Dr. Nick Gans, Electrical Engineering, University of Texas at Dallas.
		\newline
		\textsf{Control Systems, Systems Identification, State Estimation and Computer Vision.}
	}
	%
	\cvitem{Summer '16}{\bf{Hardware Integration Intern}, Amazon Robotics LLC. %Dr. Tye Brady (CTO).
		\newline
		\textsf{SLAM, Software and Hardware Integration.}
	}
	%
	\cvitem{Spring '16}{\bf{Hardware Integration Intern}, Advanced Robotics Lab, Amazon Robotics LLC. 
		\newline
		\textsf{Computer Vision, Hardware Integration.}
	}
	%%
	\subsection{Teaching:}
	\cventry{Fall '14 - '16}{Teaching Assistant, \textbf{Introduction to Robotics}}{University of Texas at Dallas}{}{}{Guided students during laboratories in programming the Robai Cyton 300R2 Robot and graded homeworks.}
	%
	\cventry{Spring '15}{\textbf{Teaching Assistant, Linear Systems (M.S. Class)}}{University of Texas at Dallas}{}{}{Responsible for helping Masters students with linear control theory applications; graded homeworks and midterms.}
	%
	\cventry{Spring '14}{\textbf{Instructor, Analysis and Design of Digital Systems}}{Adekunle Ajasin University}
	{}{}{Developed course modules, sole instructor for sophomore students, graded homeworks, designed and graded exams.}
	%
	\cventry{Summer '14}{\textbf{Instructor, Digital Logic Design}}{Adekunle Ajasin University}{}{}{Co-developed course modules, joint-instructor for junior students, graded homeworks, designed and graded exams.}
	%
	\subsection{Miscellaneous:}
	\cventry{2009--2011}{\textbf{Warehouse Manager, Apapa Plant}}{Coca-Cola Hellenic Bottling Company Plc}{Lagos}{}{}
	%
	\cventry{2007--2008}{Banking Assistant}{First Bank of Nigeria Plc}{Lagos}{}{}
	%
	\cventry{2005--2007}{System Engineer}{DMT Technologies Limited}{KD}{Nigeria}{}
	%
	%	\clearpage
