	\section{Select OpenSource Projects}
	\cvitem{\href{https://github.com/lakehanne/LyapunovLearner}{\textcolor{light-blue}{Lyapunov-Learner}}}{Python Implementation of ``Learning Control Lyapunov Functions for Dynamical Systems". (Available at \href{https://github.com/lakehanne/LyapunovLearner}{\textcolor{light-blue}{https://github.com/lakehanne/LyapunovLearner}})
	}	
	%	
	\cvitem{\href{https://github.com/lakehanne/awesome-neurocontrol}{\textcolor{light-blue}{Awesome-NeuroControl}}}{A curated list of neural applications in control theory and practice. (Available at \href{https://github.com/lakehanne/awesome-neurocontrol}{\textcolor{light-blue}{https://github.com/lakehanne/awesome-neurocontrol}})
	}		
	%			
	\cvitem{\href{https://github.com/PointCloudLibrary/pcl/pull/1827}{\textcolor{light-blue}{PCL}}}{Fix for segfault in our-cvfh algorithm in the point-cloud library. (Available at \href{https://github.com/PointCloudLibrary/pcl/pull/1827}{\textcolor{light-blue}{PR 1827}})
	}
	%
	\cvitem{\href{https://github.com/lakehanne/gps}{\textcolor{light-blue}{GPS}}}{Catkinized version of Levine et. al's guided policy search algorithm in ROS Indigo (Available at \href{https://github.com/lakehanne/gps}{\lb{https://github.com/lakehanne/gps}}). Dockerized version available at \href{https://hub.docker.com/r/lakehanne/gps/}{\lb{gps-docker}}.
	}
	%
	\cvitem{\href{https://github.com/lakehanne/keyence}{\textcolor{light-blue}{Keyence}}}{Minimal source code for retrieving profile map from the keyence LJV-7000 series line scanners. (Available at  \href{https://github.com/lakehanne/keyence}{\textcolor{light-blue}{https://github.com/lakehanne/keyence})
	}}
	%
	\cvitem{\href{https://github.com/Element-Research/rnn/blob/master/FastLSTM.lua}{\textcolor{light-blue}{RBN}}}{Recurrent Batch Normalization of Neural Networks in Torch7. (Available at \href{https://github.com/Element-Research/rnn/blob/master/FastLSTM.lua}{\textcolor{light-blue}{https://github.com/element-research/rnn}})
	}
	%
	\cvitem{\href{https://github.com/lakehanne/nn/blob/master/DICECriterion.lua}{\textcolor{light-blue}{DICE}}}{S\o{}rensen-Dice coefficients in Torch7. (Available at  \href{https://github.com/lakehanne/nn}{\textcolor{light-blue}{https://github.com/lakehanne/nn}).
	}}
	%		
	\cvitem{\href{https://github.com/lakehanne/FARNN}{\textcolor{light-blue}{FARNNs}}}{Training of multilayer networks, simple recurrent neural networks, long short-term memory cells (with peep-hole connections), fast LSTMS, %(which are LSTMs with gates computed in one fell-swoop
	and recurrent batch normalized FastLSTMs to model the relationship between Borel measurable sets. (Available at  \href{https://github.com/lakehanne/FARNN}{\textcolor{light-blue}{https://github.com/lakehanne/FARNN})
	}}
				
%	\cvitem{An all-convolutional network}{Source codes for my entry in the Kaggle 2016 data science competition in identifying and segmenting ultrasound images of the human neck. Codes available upon request.}
				