	\section{Publications}
	%
%	\vspace{0.5em}
%	%
%	\subsection{Journals Under Review}
%	\cvitem{}{\textbf{Olalekan Ogunmolu}, Michael Folkerts, Dan Nguyen, Nicholas Gans, Steve Jiang.  \href{}{\bl{Deep BOO 2.0: End-to-End Training of Beam Orientation Selection Policies for Intensity Modulated Radiation Therapy}}. Under publication invitation review at \textit{\href{https://www.springer.com/series/15556}{\bl{International Journal of Robotics Research}}} (\emph{IJRR}), 2018.}{}
%	%
%	\vspace{0.5em}
%	%
%	\subsection{Journals under prepraration}
%	\cvitem{}{\textbf{Olalekan Ogunmolu}, Michael Folkerts, Dan Nguyen, Nicholas Gans, Steve Jiang. \href{}{\bl{Deep BOO: End-to-end training of beam orientation selection policies for intensity modulated radiation therapy.}}.  IEEE Transactions on Neural Systems and Rehabilitation Engineering. 2018.}{}
%%	%
%	\cvitem{}{\textbf{Olalekan Ogunmolu}, Ayaka Kume, Jethro Tan. \href{}{\bl{A stable Lyapunov approach for designing deep policies for complex robot motion tasks}}.  Robotics and Automation Letters/International Conference on Robotics and Automation (RA-L). 2019.}{}
%	%
%	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nick Gans, Xuejun Gu, and Steve Jiang. \href{}{\bl{Simulation and control of a head and neck patient pose correction soft-robot mechanism in intensity modulated radiotherapy}}.  Transactions on Robotics (T-RO) 2018/2019.}{}
%
%	\vspace{0.5em}		
	\subsection{Refereed Conference Papers}
	\cvitem{}{Top-tier IEEE, Algorithmic Foundations of Robotics, Radiation Therapy, Medical Physics, and Machine Learning conferences, i.e., WAFR, IROS, NIPS, and ICRA are highly selective venues for archival papers only, comparable to many IEEE journals in selectivity, visibility and impact.}
	%
	\cvitem{}{Azar Sadeghnejad Barkousaraie,  \textbf{Olalekan Ogunmolu}, Steve Jiang, and Dan Nguyen.  \href{}{\bl{Deep Learning Neural Network for Beam Orientation Optimization}}. Under review at \textit{\bl{\href{http://iccr-mcma.org/iccr2019/}{International Conference on the use of Computers in Radiation Therapy XVI}}} (\emph{ICCR}), Montreal, CA. June 2019.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Azar Sadeghnejad Barkousaraie, Dan Nguyen, Nicholas Gans, and Steve Jiang.  \href{}{\bl{A Monte Carlo Tree Game for Beam Orientation Optimization}}. Under review at \textit{\bl{\href{https://iccr-mcma.org/mcma2019/}{International Conference on Monte Carlo Techniques for Medical Applications II}}} (\emph{MCMA}), Montreal, CA. June 2019.}{}
	%	
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Michael Folkerts, Dan Nguyen, Nicholas Gans, and Steve Jiang.  \href{}{\bl{Deep BOO: Automating Beam Orientation Selection in Intensity Modulated Radiation Therapy}}. To appear at \textit{\bl{\href{http://algorithmic-robotics.org/wafr2018/}{Algorithmic Foundations of Robotics XIII, International Workshop}}} (\emph{WAFR}), Mérida, Mexico. December 2018.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nicholas Gans, Tyler Summers. \href{}{\bl{Minimax Iterative Dynamic Game: Application to Nonlinear Robot Control Tasks}}. \textit{IEEE/RSJ International Conference on Intelligent Robots and Systems} (\emph{IROS}), Madrid, Spain. October 2018. DOI: 10.1109/IROS.2018.8594037}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Dan Nguyen, Xun Jia, Weiguo Lu, Nick Gans, and Steve Jiang. \href{}{\bl{Automating Beam Orientation Optimization for IMRT Treatment Planning: A Deep Reinforcement Learning Approach}}. 
	\newline
	Selected for Oral Presentation at the \textit{John R. Cameron Young Investigators Symposium -- 60th Annual Meeting of the American Association of Physicists in Medicine}, Nashville, TN (\emph{AAPM}). July 2018.}{}
	% }x
  %
	\cvitem{}{Yara Almubarak, Joshi Aniket, \bf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, Nicholas Gans, and Yonas Tadesse, \bl{Design and Development of Soft Robots for Head and Neck Cancer Radiotherapy.} \emph{\href{http://spie.org/conferences-and-exhibitions/smart-structures/nde?SSO=1}{\bl{SPIE: Smart Structures + Nondestructive Evaluation}},} Denver, CO, U.S.A. March 2018.
		}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Adwait Kulkarn, Yonas Tadesse, Xuejun Gu, Steve Jiang, and Nick Gans. \href{https://arxiv.org/abs/1703.03821}{\bl{Soft-NeuroAdapt: A 3-DOF Neuro-Adaptive Pose Correction System For Frameless and Maskless Cancer Radiotherapy}}. \textit{IEEE/RSJ International Conference on Intelligent Robots and Systems} (\emph{IROS}), Vancouver, BC, Canada. September 2017. DOI: 10.1109/IROS.2017.8206211.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nick Gans. \href{http://ecs.utdallas.edu/~opo140030/media/Papers/CASE2016/CASE2016.pdf}{\bl{Vision-based control of a soft-robot for Maskless Cancer Radiotherapy}}. \emph{IEEE Conference on Automation Science and Engineering (CASE)}, Fort-Worth, Texas, August 2016. %\newline
		DOI: 10.1109/CoASE.2016.7743378.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nick Gans. \href{http://ecs.utdallas.edu/~opo140030/media/Papers/CASE2015/CASE2015.pdf}{\bl{A Real-Time Soft-Robotic Patient Positioning System for Maskless Head-and-Neck Cancer Radiotherapy}}. \emph{IEEE Conference on Automation Science and Engineering (CASE)}, Gothenburg, Sweden, August 2015. DOI: 10.1109/CoASE.2015.7294318.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu},
		{\bl{Autonomous Navigation of a Rotor-craft unmanned aerial vehicle using machine vision.}} . \newline {MS Thesis, August. 2011. Advisor: Tony J. Dodd, University of Sheffield, England.}}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, \href{http://lakehanne.github.io/downloads/BS_Thesis.pdf}{\bl{Single Fractional Parentage Coefficients in the sd-Shell Nuclei}} . \newline {BS Thesis, Nov. 2004. \hspace{0.5em} Advisor: Ademola Amusa, Adekunle Ajasin University, Nigeria.}}{}

	%\newpage
	\section{\textbf{Abstracts}:}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nicholas Gans, Tyler Summers. \href{}{\bl{Minimax Iterative Dynamic Game: Application to Nonlinear Robot Control Tasks}}. \emph{IEEE International Conference on Robotics and Automation, \href{http://www.cs.unm.edu/amprg/Workshops/MLPC18/index.html}{\bl{Machine Learning for Planning and Control Workshop}} Extended Abstract } (\emph{ICRA 2018}), Madrid, Spain. October 2018.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nicholas Gans, Tyler Summers \bl{Minimax Iterative Dynamic Game: Application to Nonlinear Robot Control Tasks.},  \emph{IEEE International Conference on Robotics and Automation, Late Breaking Result Abstract} Brisbane, Australia, May 2018.}

	\cvitem{}{Yara Almubarak, Joshi Aniket, \bf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, Nicholas Gans, and Yonas Tadesse, \bl{Design and Development of Soft Robots for Head and Neck Cancer Radiotherapy.} \emph{\href{http://spie.org/conferences-and-exhibitions/smart-structures/nde?SSO=1}{\bl{SPIE: Smart Structures + Nondestructive Evaluation}},} Denver, CO, U.S.A. March 2018.
	}

	\cvitem{}{Tyler Summers, \textbf{Olalekan Ogunmolu}, Nicholas Gans. \bl{Robustness Margins and Robust Guided Policy Search for Deep Reinforcement Learning"}. \emph{IROS 2017 Abstract Only Track}, Vancouver, BC, Canada. September 2017.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nick Gans, Steve Jiang, Xuejun Gu. \href{http://www.aapm.org/meetings/2015AM/PRAbs.asp?mid=99&aid=29621}{\textcolor{blue}{An Image-Guided Soft Robotic Patient Positioning System for Maskless Head-And-Neck Cancer Radiotherapy: A Proof-of-Concept Study}}. \emph{American Association of Physicists in Medicine (AAPM)} Annual Meeting, Annaheim, CA, USA. July 2015.}{}

	\section{Tech Reports:}
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nicholas Gans, Tyler Summers. \href{}{\bl{\href{https://arxiv.org/abs/1710.00491}{Robust Zero-Sum Deep Reinforcement Learning}}}. \emph{arxiv PrePrints, arxiv ID:1710.00491}, Oct 2017.}{}

	%\cvitem{}{\textbf{Olalekan Ogunmolu}. \href{https://arxiv.org/abs/1612.01607v2}{\textcolor{blue}{Review of "Continuous Finite-Time Stabilization of Translational and Rotational Double Integrators"}}. \emph{arxiv PrePrints, arxiv ID: 1612.01607v2}, May 2015.}{}
