%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\PassOptionsToPackage{pdfpagelabels=false}{hyperref} 
\documentclass[10pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue, modroman]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem
	
\usepackage[sc]{mathpazo}
\linespread{1.05}
\usepackage[T1]{fontenc}
%\usepackage[dvipsnames]{xcolor}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
%\usepackage{hyperref}
% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

\setlength{\topmargin}{-0.7in}
\usepackage{calc}
\setlength{\textheight}{\textheight+0.5in}
\usepackage{layout}
%\usepackage{hyperref}
\usepackage{color}
%\hypersetup{linkbordercolor = green}
%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{Olalekan}
\familyname{Ogunmolu}
\definecolor{light-blue}{rgb}{0.30,0.35,1}
\title{Robotics | Control Systems  | AI \newline
\bf{\lb{\footnotesize 
Rerum Cognoscere Causas: To know the causes of things.} }}                               % optional, remove/comment the line if not wanted
\address{ATC 1.801, ATEC Bldg}{UT Dallas, Richardson, TX 75080}         % optional, remove/comment the line if not wanted; the "country" arguments can be omitted or provided empty 
%\fax{fax number}                             % optional, remove/comment the line if not wanted
\email{patlekano@gmail.com}  
\mobile{omitted intentionally}                             % optional, remove/comment the line if not wanted
%\homepage{http://lakehanne.github.io}                         % optional, remove/comment the line if not wanted
%\extrainfo{\footnotesize http://ecs.utdallas.edu/$\sim$olalekan.ogunmolu/} 
\extrainfo{\footnotesize http://ecs.utdallas.edu/ $\sim$ opo140030}                 % optional, 
\include{def}
	
	
\begin{document}
	\long\def\/*#1*/{}								
	\makecvtitle
	\section{Education}
	\cventry{2014--Present}{PhD in Electrical Engineering }{University of Texas at Dallas}{Richardson}{United States}
	{Advisor: Prof. Nick Gans. Design and prototype of a medical soft robot for automated patient positioning during cancer radiotherapy. {}   } % arguments 3 to 6 can be left empty
	%
	\cventry{2011--2012}{Master of Science in Engineering in Control Systems}{The University of Sheffield}{Sheffield}{United Kingdom}{Advisor: Prof. Tony J. Dodd. Thesis: ``\href{http://lakehanne.github.io/downloads/MS_Thesis.pdf}{\textcolor{blue}{Autonomous Navigation of a Rotorcraft Unmanned Aerial Vehicle using Machine Vision}}.'' | Committee Members: Drs. George Panoutsos and Robin Pursehouse. | Dissertation reviewed by Prof. Mahdi Mahfouf.}
	%
	\cventry{2000--2005}{Bachelor Of Science in Physics \& Electronics}{Adekunle Ajasin University}{Akungba}{Nigeria}{\href{http://lakehanne.github.io/downloads/BS_Thesis.pdf}{\textcolor{blue}{Senior thesis}} advised by Prof. Ademola Amusa (\emph{MS, Columbia University, PhD UIUC}).| Dissertation Grade: 85\% $\equiv$ A+ | Graduated Magna Cum Laude.}
	%

	\section{Publications}
	\subsection{\textit{\underline{Peer-Reviewed}}}
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Adwait Kulkarn, Yonas Tadesse, Xuejun Gu, Steve Jiang, and Nick Gans. \href{https://arxiv.org/abs/1703.03821v1}{\bl{A 3-DOF Neuro-Adaptive Pose Correction System For Frameless and Maskless Cancer Radiotherapy}}. \textit{IEEE/RSJ International Conference on Robots and Systems} (\emph{IROS 2017}), Vancouver, BC, Canada. September 2017.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nick Gans. \href{http://ecs.utdallas.edu/~opo140030/media/Papers/CASE2016/CASE2016.pdf}{\bl{Vision-based control of a soft-robot for Maskless Cancer Radiotherapy}}. \emph{IEEE Conference on Automation Science and Engineering (CASE)}, Fort-Worth, Texas, August 2016. %\newline
	 DOI: 10.1109/CoASE.2016.7743378}{}
	%	
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nick Gans. \href{http://ecs.utdallas.edu/~opo140030/media/Papers/CASE2015/CASE2015.pdf}{\bl{A Real-Time Soft-Robotic Patient Positioning System for Maskless Head-and-Neck Cancer Radiotherapy}}. \emph{IEEE Conference on Automation Science and Engineering (CASE)}, Gothenburg, Sweden, August 2015. DOI: 10.1109/CoASE.2015.7294318}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nick Gans, Steve Jiang, Xuejun Gu. \href{http://www.aapm.org/meetings/2015AM/PRAbs.asp?mid=99&aid=29621}{\textcolor{blue}{An Image-Guided Soft Robotic Patient Positioning System for Maskless Head-And-Neck Cancer Radiotherapy: A Proof-of-Concept Study}}. \emph{American Association of Physicists in Medicine (AAPM)} Annual Meeting, July 2015.}{}
	%
	\cvitem{}{\textbf{Olalekan Ogunmolu}, %\href{http://lakehanne.github.io/downloads/MS_Thesis.pdf}
	{\bl{Autonomous Navigation of a Rotor-craft unmanned aerial vehicle using machine vision.}} . \newline {MS Thesis, August. 2011. Advisor: Tony J. Dodd, University of Sheffield, England.}}{}
	%	
	\cvitem{}{\textbf{Olalekan Ogunmolu}, \href{http://lakehanne.github.io/downloads/BS_Thesis.pdf}{\bl{Single Fractional Parentage Coefficients in the sd-Shell Nuclei}} . \newline {BS Thesis, Nov. 2004. \hspace{0.5em} Advisor: Ademola Amusa, Adekunle Ajasin University, Nigeria.}}{}
	
	\subsection{\textit{\underline{Tech Reports}}}
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, Nicholas Gans. \href{https://arxiv.org/abs/1610.01439}{\bl{Nonlinear Systems Identification Using Deep Dynamic Neural Networks"}}. \emph{arxiv PrePrints, arxiv ID:1610.01439}, Oct 2016.}{}
	
	\cvitem{}{\textbf{Olalekan Ogunmolu}. \href{https://arxiv.org/abs/1612.01607v2}{\textcolor{blue}{Review of "Continuous Finite-Time Stabilization of Translational and Rotational Double Integrators"}}. \emph{arxiv PrePrints, arxiv ID: 1612.01607v2}, May 2015.}{}
	
		\section{Experience}
		\subsection{\itu{Research}}
		\cvitem{Summer '17}{\bf{Research Assistant}, Dr. Tyler Summers, Mechanical Engineering, UT Dallas.
			\newline
			\textsf{Dynamic Programming, Decision Theoretic Control, Machine/Reinforcement Learning.}	}
		%
		\cvitem{Fall '14 - Present}{\bf{Research Assistant}, Dr. Nick Gans, Electrical Engineering, University of Texas at Dallas.
			\newline
			\textsf{Control Systems, Systems Identification, State Estimation and Computer Vision.}
		}
		%
		\cvitem{Summer '16}{\bf{Hardware Integration Intern}, Amazon Robotics LLC. Dr. Tye Brady (CTO).
			\newline
			\textsf{SLAM, Software and Hardware Integration.}
		}
		%
		\cvitem{Spring '16}{\bf{Hardware Integration Intern}, Advanced Robotics Lab, Amazon Robotics LLC.  Dr. Andy Stubbs (Sr. Systems Manager).
			\newline
			\textsf{Computer Vision, Hardware Integration.}
		}
		%%
		\subsection{\itu{Teaching}}
		\cventry{Fall '14 - '16}{Teaching Assistant, \textbf{Introduction to Robotics}}{University of Texas at Dallas}{}{}{Guided students during laboratories in programming the Robai Cyton 300R2 Robot and graded homeworks.}
		%
		\cventry{Spring '15}{\textbf{Teaching Assistant, Linear Systems (M.S. Class)}}{University of Texas at Dallas}{}{}{Responsible for helping Masters students with linear control theory applications; graded homeworks and midterms.}
		%
		\cventry{Spring '14}{\textbf{Instructor, Analysis and Design of Digital Systems}}{Adekunle Ajasin University}
		{}{}{Developed course modules, sole instructor for sophomore students, graded homeworks, designed and graded exams.}			
		%
		\cventry{Summer '14}{\textbf{Instructor, Digital Logic Design}}{Adekunle Ajasin University}{}{}{Co-developed course modules, joint-instructor for junior students, graded homeworks, designed and graded exams.}
		%
		\subsection{\itu{Miscellaneous}	}
		\cventry{2009--2011}{\textbf{Warehouse Manager, Apapa Plant}}{Coca-Cola Hellenic Bottling Company Plc}{Lagos}{}{}
		%
		\cventry{2007--2008}{Banking Assistant}{First Bank of Nigeria Plc}{Lagos}{}{}
		%
		\cventry{2005--2007}{System Engineer}{DMT Technologies Limited}{KD}{Nigeria}{}
		%
	%	\clearpage
		
	\section{Invited Talks}
	\cvitem{UTSW, Dallas, TX}{\bl{\href{http://scr.tamu.edu/?page_id=687}{A 3-DOF Neuro-Adaptive Patient Pose Correcting System For Frameless and Maskless Cancer Radiotherapy}},  \emph{Physics Research Seminar Series, Radiation Oncology Department, UT Southwestern Medical Center,} Dallas, TX, USA. March 2017.}
		
	\cvitem{IEEE Arlington, TX}{\bl{Towards automated accurate patient positioning in maskless cancer radiotherapy}. \emph{IEEE Computational Intelligence Society,} UT Arlington, TX, USA. December 2015.}
	
	\section{Poster Presentations}
	\cvitem{Texas Systems Day}{\bf{A 3-DOF Neuro-Adaptive Pose Correction System For Frameless and Maskless Cancer Radiotherapy},  \emph{Texas Systems Day, Texas A \& M University,} College Station, TX, USA. March 2017.}
			
	\section{Mentoring}
	\subsection{\itu{Undergraduate mentoring}}
	\cvline{Summer 2017}{Rachael Thompson. MIT Freshman (Starting in Fall 2017); Sleiman Safaoui. UTD Senior.}{}
	\cvline{2016 - Now }{Alex Tomkovich. Computer Engineering Junior.}{}
	\cvline{Spring 2015}{Grant Carr. Computer Engineering Junior.}{}
		
	\subsection{\itu{Masters Mentoring}}
	\cvline{2016 -- 2017}{Adwait Kulkarn. Mechanical Engineering Masters student (Currently at Drov Technologies, MN).
			}{}
	\cvline{2015}{Ajith Venkateswaran. Computer Engineering Masters student (Currently at Samsung Research, America).}{}
					
		
	\section{Languages}
	\cvitemwithcomment{English}{Can read, write and speak fluently.}{Lived in Nigeria, United Kingdom and United States.}
		
	\cvitemwithcomment{Yoruba}{Proficient}{Native Nigerian Language. Spoken at home.}

	\section{Awards and honors}	
	\cvlistitem{President’s \bf{Teaching Excellence Award} for Teaching Assistants (UTD) \hspace{0.9em}	 Nom. Feb. 2017}
	
	\cvlistitem{\bf{Golden Key International Honour Society} \hspace{11.6em} Inducted Dec. 2016}		
	
	\cvlistitem{\textbf{IEEE RAS Travel Award} \hspace{8.1cm} August 2016}	
			
	\cvlistitem{\textbf{Ericsson Graduate Fellowship} \hspace{7.4cm} 2015 - 2016}	
	
	\cvlistitem{\textbf{Jonsson Scholarship} \hspace{8.8cm} 2014 - 2015}	
		
	\cvlistitem{\textbf{Achievement Award, University of Florida }
	\textit{(Declined)} \qquad \qquad \qquad \qquad \qquad \quad Fall 2014  }	
		
	\cvlistitem{\textbf{PTDF Overseas Scholarship Award} 
	%\emph{\textbf{\pounds25,500+ for one year}.}
	\qquad \qquad \hspace{1.0cm} ($\sim$1.7\% acceptance) 	
	\hspace{2.0cm} 2011 
}
	%\cvitem{}{\footnotesize Competitive, merit-based scholarships awarded to best 5 students from each state in the country. Second ranked awardee from my state in nation-wide tests. \emph{\textbf{\pounds25,500+ for one year}.}}
		
	\cvlistitem{\textbf{Federal Government (of Nigeria) Scholarship} \hspace{0.9cm}  ($\sim$3.6\%  acceptance)\hspace{1.7cm}	2002}
	%\cvitem{}{\footnotesize Competitive, merit-based scholarships awarded to best Nigerian students based on performance in questions relating to science and engineering. \emph{\textbf{N50,000 per annum}}.}
		
	\cvlistitem{\textbf{Ondo State (Nigeria) Scholarship} \hspace{2.8cm} ($\sim$10\% acceptance) \hspace{2.0cm} 2004}
	%\cvitem{}{Merit-based scholarship for Ondo state students with excellent academic achievement and honors grade. \emph{\textbf{N25,000}} per annum.} 
	
	\section{Select services and leadership}
	\cventry{June 17-Now}{Member}{}{\bf{IEEE Robotics and Automation Society}}{[Member ID: 92127153]}{}
	
	\cventry{June 2017}{Invited Contributor}{IEEE/RSJ  IROS Conference Abstract Only Track}{Vancouver}{BC}{}
		
	\cventry{Jan. 2017}{Reviewer}{\textbf{\textit{IFAC}}}{International Federation of Automatic Control World Congress}{}{}
	
	\cventry{March. 2017}{Open Reviewer}{\textbf{\textit{ICML}}}{\href{https://arxiv.org/pdf/1703.00443.pdf}{\textcolor{light-blue}{OptNet: Differentiable Optimization as a Layer in Neural Networks}}}{}{}
	
	\cventry{2016--present}{Member}{IEEE Boston}{Greater Boston, USA}{}{}
	
	\cventry{2015 -- 2016}{Science instructor}{IEEE Dallas Shoulder of Giants Workshops}{Dallas, TX}{}{Participant at IEEE Dallas Young Professionals community outreaches in promoting STEM education and awareness in the Dallas/Fort-Worth Metroplex.}
	
	\cventry{Summer 2015}{Summer Science Program}{University of Texas at Dallas}{Richardson, TX}{}{Trained high-school kids in basic robots control and programming with the Berkeley Snap! kit and arduino.}

	\cventry{Fall 2012}{Workshop participant}{ILA Berlin Airshow}{Berlin, Germany}{}{Selected by Cassidian (an EADS company) for the \emph{Aerospace Systems Engineering} workshop. % based on a competitive admission process.
	}
	
	\cventry{Summer 2012}{Workshop participant}{Farnborough International Airshow}{NE Hampshire, England}{}{Selected by Airbus (an EADS company) among participants at the \emph{UAV and Fighter Aircraft} workshop. % based on a competitive admission process.
	}
	\section{Computing}
	\cvitem{\textcolor{light-blue}{Programming}}{ C++, Python, Lua, MATLAB, LabVIEW.}
	%
	\cvitem{\lb{Libraries}}{Point Cloud Library, OpenCV, Torch7, Eigen, Docker, Google Cloud Compute, AWS S3, AWS EC2, PyTorch, OpenAI Gym, MuJoCo, Numpy, SciPy, Scikit-Learn, C++11/14 standards.
	} 
	%
	\cvitem{\lb{OS}}{Ubuntu, Debian, Windows.}
	%
	\cvitem{\lb{OSRF}}{ROS hydro, indigo, jade, and kinetic distros. Xacro, urdfs, pr2 robot packages, gazebo, urdfdom-py, ros-control, message filters, eigen, tf, tf2, hector-quadrotor, kdl, slam-gmapping, rviz, rqt, amcl, orocos, controller-manager,  geometry-msgs, rosaria, ros-arnl, sensor-msgs, nav stack. Familiar with staubli TX-90 and ur10 robot packages.
	}
	%
	\cvitem{\textcolor{light-blue}{\small Web}}{{\small HTML}, {\small Markdown,  socket.io, node.js, and express.js.}
	}
	
	\section{Select OpenSource Projects}	 
 	  	 
 	 \cvitem{\href{https://github.com/lakehanne/savitzky-golay}{\textcolor{light-blue}{Savgol}}}{C++ Implementation of Savitzky-Golay Differentiation Coefficients and Filters. (Available at \href{https://github.com/lakehanne/savitzky-golay}{\textcolor{light-blue}{https://github.com/lakehanne/savitzky-golay}})
 	 }

 	 \cvitem{\href{https://github.com/lakehanne/gps}{\textcolor{light-blue}{GPS}}}{Catkinized version of Levine et. al's guided policy search algorithm in ROS Indigo (Available at \href{https://github.com/lakehanne/gps}{\lb{https://github.com/lakehanne/gps}}). Dockerized version available at \href{https://hub.docker.com/r/lakehanne/gps/}{\lb{gps-docker}}.
 	 }
  %
	  \cvitem{\href{https://github.com/lakehanne/keyence}{\textcolor{light-blue}{Keyence}}}{Minimal source code for retrieving profile map from the keyence LJV-7000 series line scanners. (Available at  \href{https://github.com/lakehanne/keyence}{\textcolor{light-blue}{https://github.com/lakehanne/keyence}) 
	  	}}
	  	%
  	  \cvitem{\href{https://github.com/element-research/rnn}{\textcolor{light-blue}{RBN}}}{Recurrent Batch Normalization of Neural Networks in Torch7. (Available at \href{https://github.com/element-research/rnn}{\textcolor{light-blue}{https://github.com/element-research/rnn}})
  	  	 }
  	 %
 	 \cvitem{\href{https://github.com/lakehanne/nn/blob/master/DICECriterion.lua}{\textcolor{light-blue}{DICE}}}{S\o{}rensen-Dice coefficients in Torch7. (Available at  \href{https://github.com/lakehanne/nn}{\textcolor{light-blue}{https://github.com/lakehanne/nn}). 
 	  	 	}}	
   
 	\cvitem{\href{https://github.com/lakehanne/FARNN}{\textcolor{light-blue}{FARNNs}}}{Training of multilayer networks, simple recurrent neural networks, long short-term memory cells (with peep-hole connections), fast LSTMS, %(which are LSTMs with gates computed in one fell-swoop
 	and recurrent batch normalized FastLSTMs to model the relationship between Borel measurable sets. (Available at  \href{https://github.com/lakehanne/FARNN}{\textcolor{light-blue}{https://github.com/lakehanne/FARNN})
 	}} 	
 	
 %	\cvitem{An all-convolutional network}{Source codes for my entry in the Kaggle 2016 data science competition in identifying and segmenting ultrasound images of the human neck. Codes available upon request.}

\iffalse 		
	\section{Other interests and activities}

	\cvline{}{Most-viewed writer in ROS, \textbf{\textit{Quora}} \hspace{10em}
	%\newline 
	\textsf{ June - August, Nov-Jan 2016-2017}}{}
	
	\cvline{}{Most-viewed writer in Control Engineering, \textbf{\textit{Quora}}
%	\newline
	\hspace{10.8em} \textsf{ 2015 - Present}
	}{}
	

	\cvline{}{Teacher Badge \hspace{9.0em}\textbf{\textit{Stackoverflow.com}}
	%	\newline
	\hspace{10.0em}\textsf{2015 -- Present}}{}
	
	\cvline{}{Scholar Badge \hspace{9.0em}\textbf{\textit{Stackexchange.com}}
		%	\newline
	\hspace{10.0em}\textsf{2015 -- Present}}{}
\fi
	\renewcommand{\listitemsymbol}{-}
	\clearpage
	%-----       letter       ---------------------------------------------------------
	% recipient data
%	\recipient{Company Recruitment team}{Company's name\\Street address\\Zip Code City}
%	\date{Date}
%	\opening{Dear Sir or Madam,}
%	\closing{Yours faithfully,}
%	\enclosure{enclosures}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%	\makelettertitle
%	\makeletterclosing

\end{document}
